---
title: "Rpath using R Ecosystem"
author: "Ralien Purco"
date: "`r Sys.Date()`"
---

# Test for productivity hypothesis (H10 EWE software)


```{r, echo = F}
# Install package


remove.packages("Rpath")
remotes::install_github('Purco/Rpath_fork')
```

```{r rpath load, echo = F}
# Run package
library(Rpath); library(data.table)
```


```{r}
# Run package for combination
library(gtools) 
# Generate all possible combinations of 4 values that sum to 100
combinations <- permutations(n = 100, r = 4, v = 1:100)

# Filter valid combinations (sum to 100)
valid_combinations <- subset(combinations, rowSums(combinations) == 100)

valid_combinations <-as.data.frame(valid_combinations)

valid_combinations$scenario<-paste("scenario",rownames(valid_combinations),sep="")

library(tidyverse)

valid_combinations=valid_combinations %>%pivot_longer(cols=c(1:4),names_to = "sp_scn", values_to = "prc_scn")

data.valid_combinations=as.data.frame(valid_combinations)

list_combinations=list()
scenarios<-unique(data.valid_combinations$scenario)

for (i in 1:length(scenarios)) {
 list_combinations[[i]]=subset(data.valid_combinations,scenario==scenarios[i])
}


list_comb=list_combinations
```


# Add data


```{r,echo=FALSE,warning = FALSE,message = FALSE}
# define list of packages in vector
package<-c("readxl")

# define function to load all packages
instal<-function(x){ 
  for(pkg in x){
  instal=require(pkg, character.only = T) # load package x 
}}
instal(package) # load list of packages in vector package

```

```{r,include=FALSE,warning = FALSE,message = FALSE}
# set working directory
# setwd("C:/Users/prralien/Nextcloud/RENK/A_Purco/Thèse_Purco/Ecopath_R/Rpath_fork")

# Import data
# data_ini<-read_excel("Stocking_Hypothesis.xlsx",sheet = 1)
```


```{r,include=FALSE,warning = FALSE,message = FALSE}
data_ini.ad<-read_excel("Stocking_Hypothesis_ad.xlsx",sheet = 1)
data_ini.juv<-read_excel("Stocking_Hypothesis_juv.xlsx",sheet = 1)
data_ini.Rgroup<-read_excel("Stocking_Hypothesis_Rgroup.xlsx",sheet = 1)
```


```{r}
list_comb.d=list()
for (i in 1:length(scenarios)) {
 list_comb.d[[i]]=cbind(data_ini.ad,list_comb[[i]])
}

for (i in 1:length(scenarios)) {
 list_comb.d[[i]]=rbind(list_comb.d[[i]],data_ini.juv)
}
```


####

# Calcul
```{r}
for (i in 1:length(scenarios)) {

# For adult group

list_comb.d[[i]]$WT_Stk=list_comb.d[[i]]$prc_scn/100*list_comb.d[[i]]$Stocking_Tot #Calcul initial biomass by percentage in sceanrio (Stocking total fix)

list_comb.d[[i]]$Nb_Stk=list_comb.d[[i]]$WT_Stk/list_comb.d[[i]]$Wi_Stk #Calcul initial number of species

list_comb.d[[i]]$Wf_F=list_comb.d[[i]]$Wi_Stk*exp((list_comb.d[[i]]$SGR*list_comb.d[[i]]$Duration)/100)   #Calcul final Weight mean by SGR and duration (= 270 day)

list_comb.d[[i]]$Nb_F=(1-list_comb.d[[i]]$Mortality/100)*list_comb.d[[i]]$Nb_Stk #Calcul final number by mortality rate

list_comb.d[[i]]$WT_F=list_comb.d[[i]]$Nb_F*list_comb.d[[i]]$Wf_F #Calcul final biomass

# For juvenil group

list_comb.d[[i]]$Wf_F[5]=4.30 #Fix initial weight of Roach_juv 
list_comb.d[[i]]$Wf_F[6]=5.60 #Fix initial weight of Tench_juv 

list_comb.d[[i]]$Nb_F[5]=list_comb.d[[i]]$Nb_Stk[3]*72 # #Calcul final number of Roach-juv by multiplying the number of adults by 72 (fix including mortality ) 
list_comb.d[[i]]$Nb_F[6]=list_comb.d[[i]]$Nb_Stk[4]*108 # #Calcul final number of Tench-juv by multiplying the number of adults by 108 (fix including mortality ) 

list_comb.d[[i]]$WT_F[5]=list_comb.d[[i]]$Wf_F[5]*list_comb.d[[i]]$Nb_F[5] #Calcul final biomass of Roach_juv 
list_comb.d[[i]]$WT_F[6]=list_comb.d[[i]]$Wf_F[6]*list_comb.d[[i]]$Nb_F[6]   #Calcul final biomass of Tench_juv

list_comb.d[[i]]$Prc_F=list_comb.d[[i]]$WT_F/sum(list_comb.d[[i]]$WT_F)*100 #Calcul final percentage by species

list_comb.d[[i]]$Rdt.net=((list_comb.d[[i]]$WT_F-list_comb.d[[i]]$WT_Stk)/1000)/0.1 # Yield net kg/ha (by pond surface 0.1 ha)

# Duplicate the scenario name
list_comb.d[[i]]$scenario[c(5:6)]=list_comb.d[[i]]$scenario[1]

list_comb.d[[i]]$Z=-(log(list_comb.d[[i]]$Nb_F/list_comb.d[[i]]$Nb_Stk))#Calcul Z

list_comb.d[[i]]$Nb.mean=(list_comb.d[[i]]$Nb_Stk-list_comb.d[[i]]$Nb_F)/list_comb.d[[i]]$Z#Calcul mean number

list_comb.d[[i]]$W.mean=(list_comb.d[[i]]$Wi_Stk+list_comb.d[[i]]$Wf_F)/2 #Calcul mean weight

# Calcul mean biomass for adult group
list_comb.d[[i]]$B.g=list_comb.d[[i]]$Nb.mean*list_comb.d[[i]]$W.mean
# Calcul mean biomass for juvenil group
list_comb.d[[i]]$B.g[5]=list_comb.d[[i]]$WT_F[5]/2 #Calcul mean biomass of Roach_juv 
list_comb.d[[i]]$B.g[6]=list_comb.d[[i]]$WT_F[6]/2 #Calcul mean biomass of Tench_juv


list_comb.d[[i]]$B.g.m2=list_comb.d[[i]]$B.g/1000 #Calcul mean biomass in g/m2

list_comb.d[[i]]$B_DW=list_comb.d[[i]]$B.g.m2*list_comb.d[[i]]$DW_rate #Calcul mean biomass in dry weight

list_comb.d[[i]]$BA.g=list_comb.d[[i]]$WT_F-list_comb.d[[i]]$WT_Stk #Calcul biomass accumulation

#Calcul P:B for adult group
list_comb.d[[i]]$`P/B`=list_comb.d[[i]]$BA.g/list_comb.d[[i]]$B.g+list_comb.d[[i]]$Z

#Calcul P:B for juv group
list_comb.d[[i]]$`P/B`[5]=list_comb.d[[i]]$BA.g[5]/list_comb.d[[i]]$B.g[5]
list_comb.d[[i]]$`P/B`[6]=list_comb.d[[i]]$BA.g[6]/list_comb.d[[i]]$B.g[6]

list_comb.d[[i]]$Bacc.g.m2=list_comb.d[[i]]$BA.g/1000 # Calcul Biomass acc in g/m2

# Calcul Biomass accumulate in dry weight
list_comb.d[[i]]$Baacc_DW=list_comb.d[[i]]$Bacc.g.m2*list_comb.d[[i]]$DW_rate

}

```


```{r}
# Add resource group
for (i in 1:length(scenarios)) {
 list_comb.d[[i]]=rbind(list_comb.d[[i]],data_ini.Rgroup)
 list_comb.d[[i]]$scenario[c(7:10)]=list_comb.d[[i]]$scenario[1]
}

```


```{r}
list_comb.d.all=list_comb.d
```

```{r}
# Put in dataframe

All_data=do.call(rbind.data.frame,list_comb.d.all)
```


#### Ecopath

```{r groups}
#Groups and types for the H10

groups <- c('Common_carp', 
            'Pike_perch', 
            'Roach',
            'Tench', 
            'Roach_juv', 
            'Tench_juv', 
            'Macroinvertebrate', 
            'Zooplancton', 
            'Phytoplancton',
            'Detritus')

types  <- c(rep(0, 8), 1, 2)
stgroups <- c(rep(0, 10))

REco.params <- create.rpath.params(group = groups, type = types,stgroup=stgroups)
```



```{r Model Table sans stanzas}
REco.params$model[, Biomass := All_data[All_data$scenario==scenarios[36314],]$B_DW]

REco.params$model[, PB := All_data[All_data$scenario==scenarios[36314],]$`P/B`]

REco.params$model[, QB := All_data[All_data$scenario==scenarios[36314],]$`C/B`]

#Biomass accumulation 
REco.params$model[, BioAcc  := c(All_data[All_data$scenario==scenarios[36314],]$Baacc_DW[c(1:4)],rep(0, 6))]
## Bio Acc for juv =0

# Unassimilated consumption
REco.params$model[, Unassim := c(rep(0.2, 6), rep(0.4, 2), rep(0, 2))]

#Detrital Fate
REco.params$model[, Detritus := c(rep(1, 9), rep(1, 1))]
```



```{r diet fill}

REco.params$diet[, Common_carp       := c(NA,NA,NA,NA, 0.01, 0.01, 0.18, 0.22,0.12,0.46,NA)]
                 
REco.params$diet[, Pike_perch        := c(NA,NA,NA,NA, 0.28, 0.02, 0.12, 0.56,NA,0.02,NA)]
 
REco.params$diet[, Roach             := c(NA,NA,NA,NA,NA,NA, 0.02, 0.25,0.14,0.59,NA)]

REco.params$diet[, Tench             := c(NA,NA,NA,NA,NA,NA, 0.22, 0.12,0.10,0.56,NA)]

REco.params$diet[, Roach_juv         := c(NA,NA,NA,NA,NA,NA, 0.01, 0.20,0.39,0.40,NA)]

REco.params$diet[, Tench_juv         := c(NA,NA,NA,NA,NA,NA, 0.01, 0.15,0.24,0.60,NA)]

REco.params$diet[, Macroinvertebrate := c(NA,NA,NA,NA,NA,NA, 0.08, 0.16,0.35,0.41,NA)]

REco.params$diet[, Zooplancton     := c(NA,NA,NA,NA,NA,NA, NA, 0.11,0.27,0.62,NA)]


```


```{r Running ecopath}
REco <- rpath(REco.params, eco.name = 'R Ecosystem')
REco
```

### Model parameters
 



Here are the rest of the columns for the model list.
```{r Model Table sans stanzas}
#Model
## Biomass
biomass <- c(1.44,
             0.56,
             1.34,
             0.93,
             0.45,
             0.16,
             0.25,
             0.54,
             1.92,
             48.81)


```








```{r Model Table sans stanzas}
All_data[All_data$scenario==scenarios[36314],]

## Production by biomass

pb <- c(1.69,
        1.52,
        0.71,
        0.48,
        2.00,
        2.00,
        14.50,
        92.43,
        118.7,
        NA)

## Consumption by biomass

qb <- c(4.93,
        2.19,
        5.09,
        5.18,
        5.29,
        5.14,
        48.33,
        308.1,
        rep(NA,2))
```



```{r}
# #Fisheries
# #Landings
# fleet <- c(rep(NA, 11))
# REco.params$model[, Fleet := fleet]
# 
# #Discards
# 
# fleet.d <- c(rep(NA, 11))
# REco.params$model[, Fleet.disc := fleet.d]
```

```{r Model Table sans stanzas}
#Biomass accumulation 
REco.params$model[, BioAcc  := c(2.28,0.83,0.93,0.43,rep(0, 6))]

# Unassimilated consumption
REco.params$model[, Unassim := c(rep(0.2, 6), rep(0.4, 2), rep(0, 2))]

#Detrital Fate
REco.params$model[, Detritus := c(rep(1, 9), rep(1, 1))]
# REco.params$model[, Discards := c(rep(0,10))]
# 
# #Fisheries
# #Landings
# trawl  <- c(rep(0, 4), 0.08, 0, 0.32, 0, 0.09, 0, 0.05, 0.2, rep(0, 10), rep(NA, 3))
# mid    <- c(rep(0, 12), 0.3, 0.08, 0.02, rep(0, 7), rep(NA, 3))
# dredge <- c(rep(0, 15), 0.1, 0.5, rep(0, 5), rep(NA, 3))
# REco.params$model[, Trawlers := trawl]
# REco.params$model[, Midwater := mid]
# REco.params$model[, Dredgers := dredge]
# 
# #Discards
# trawl.d  <- c(1e-5, 1e-7, 0.001, 0.001, 0.005, 0.001, 0.009, 0.001, 0.04, 0.001,
#               0.01, 0.08, 0.001, 0.001, 0.001, rep(0, 7), rep(NA, 3))
# mid.d    <- c(rep(0, 2), 0.001, 0.001, 0.01, 0.001, 0.01, rep(0, 4), 0.05, 0.05,
#               0.01, 0.01, rep(0, 7), rep(NA, 3))
# dredge.d <- c(rep(0, 3), 0.001, 0.05, 0.001, 0.05, 0.001, 0.05, 0.001, 0.01, 0.05,
#               rep(0, 3), 0.09, 0.01, 1e-4, rep(0, 4), rep(NA, 3))
# REco.params$model[, Trawlers.disc := trawl.d]
# REco.params$model[, Midwater.disc := mid.d]
# REco.params$model[, Dredgers.disc := dredge.d]
```

```{r Model Table final, echo = F}
knitr::kable(REco.params$model, 
             caption = 'Example of completed model list')

```

###Stanza Parameters




###Diet Parameters

Note : 
eg: REco.params$diet[Group == 'OtherGroundfish', Seabirds := 0.1]
knitr::kable(REco.params$diet[, list(Group, Seabirds, Whales)])
NA: import

Here is the completed model parameter file for R Ecosystem:

```{r diet fill}

REco.params$diet[, Common_carp       := c(NA,NA,NA,NA, 0.01, 0.01, 0.18, 0.22,0.12,0.46,NA)]
                 
REco.params$diet[, Pike_perch        := c(NA,NA,NA,NA, 0.28, 0.02, 0.12, 0.56,NA,0.02,NA)]
 
REco.params$diet[, Roach             := c(NA,NA,NA,NA,NA,NA, 0.02, 0.25,0.14,0.59,NA)]

REco.params$diet[, Tench             := c(NA,NA,NA,NA,NA,NA, 0.22, 0.12,0.10,0.56,NA)]

REco.params$diet[, Roach_juv         := c(NA,NA,NA,NA,NA,NA, 0.01, 0.20,0.39,0.40,NA)]

REco.params$diet[, Tench_juv         := c(NA,NA,NA,NA,NA,NA, 0.01, 0.15,0.24,0.60,NA)]

REco.params$diet[, Macroinvertebrate := c(NA,NA,NA,NA,NA,NA, 0.08, 0.16,0.35,0.41,NA)]

REco.params$diet[, Zooplancton     := c(NA,NA,NA,NA,NA,NA, NA, 0.11,0.27,0.62,NA)]


```

```{r Dietfile Table, echo = F}
knitr::kable(REco.params$diet, caption = 'Diet parameters for R Ecosystem')
```

```{r}
colSums(REco.params$diet[,2:length(REco.params$diet)],na.rm = T)


```



###Pedigree parameters
Rpath does not currently use pedigrees however, future Rpath extensions will use
them.  Therefore we include them in the current parameter object. The
default values are 1 (low confidence).  These defaults are not changed for R
Ecosystem but can obviously be changed in a similar manner to the other parameter
files.
```{r pedigree table, echo = F}
knitr::kable(REco.params$pedigree, caption = 'Pedigree parameters for R Ecosystem')
```

## Running Ecopath


After creating the parameter object, running ecopath in R is relatively 
straightforward.  It is just the function `rpath` supplied with the parameter object.
Additionally, you can supply an ecosystem name for the output.

```{r Running ecopath}
REco <- rpath(REco.params, eco.name = 'R Ecosystem')
REco
```

The output object from `rpath` is an S3 object type called 'Rpath'.  Rpath objects
are a list of parameters from the mass balance.  However, the `print` function will
display the same information as the "Basic Estimates" tab from EwE. You will also 
notice that the `print` function will display whether the model is balanced or not.
If the model was not balanced, it would list the groups that are not balanced.

You can also display the mortalities associated with each group by supplying the
argument `morts = T` to the `print` function.

```{r Ecopath morts}
print(REco, morts = T)
```

Note that if you wish to save the `print` output you need to use the function
`write.rpath`.  This function will also accept the argument 'morts = T'.

The generic function `summary` will display some summary statistics on the model
as well as a list of attributes you can access.  To access any of the other 
attributes simply use the standard list notation.

```{r Ecopath summaries}
summary(REco)
REco$TL
```

One of the advantages of R is its graphical ability.  Users can feel free to develop
their own graphical routines for the Rpath outputs.  However, we have included
a basic food web plot.  The routine can include fisheries, display group numbers or 
names, and even highlight a particular group.

```{r Food Web Plots, fig.align = 'center', fig.height = 7, fig.width = 7}
webplot(REco)
webplot(REco, labels = T)
# webplot(REco, fleets = T, highlight = 'AduRoundfish1')
```


####


```{r}
for (i in 1:nrow(valid_combinations)) {
 list_combinations[[i]]=subset(valid_combinations,scenario==scenarios[i])
}
```


```{r}
for (i in 1:length(scenarios)) {
     
list_comb[[1]]=t(list_comb[[1]][c(1:4)])
      
 dd[[i]]$rS_d=0
       
       dd[[i]]$rvol.sum.c=0
       dd[[i]]$rH_d=0
       
       dd[[i]]$rdvol.sum=0
       dd[[i]]$rA_d=0
}

```




```{r}
for (i in 1:length(dd)) {
       dd[[i]]$rvol.sum=0
       dd[[i]]$rS_d=0
       
       dd[[i]]$rvol.sum.c=0
       dd[[i]]$rH_d=0
       
       dd[[i]]$rdvol.sum=0
       dd[[i]]$rA_d=0
}

```



```{r,include=F,warning=F, error=FALSE, message=F}
data_1=data %>% group_by(year,espece,model,sc.clim, CO2, prop.y,GRECO.sim,sc.g,d.strss,Tm,vol.sum.c)%>%tally()%>%dplyr::select(-n)

a=data_1
a$pj=paste(a$GRECO.sim,a$sc.g,a$espece,a$prop.y,a$sc.clim,a$CO2,a$model,sep = "_")

b=unique(a$pj)

c=list()

for (i in 1:length(b)) {
  c[[i]]=subset(a,pj==b[i])
}


an=c("2020","2030","2040","2050","2060","2070","2080","2090","2095")
an1=as.numeric(an)
g=c

for (i in 1:length(g)) {
  g[[i]]=g[[i]][g[[i]]$year%in%an1,]
}

cc=c

for (i in 1:length(cc)) {
  cc[[i]]$year=as.numeric(cc[[i]]$year)
}


hh=g
for (i in 1:length(hh)) {
       hh[[i]]$d.strssm=0
       hh[[i]]$Tmh=0
}


for (i in 1:length(hh)) {
    for (k in 1:length(an1)){
    hh[[i]]$d.strssm[k]=mean(cc[[i]]$d.strss[1:(an1[k]-2009)])
}
}

for (i in 1:length(hh)) {
    for (k in 1:length(an1)){
    hh[[i]]$Tmh[k]=mean(cc[[i]]$Tm[1:(an1[k]-2009)])
}
}
```


```{r,include=F,warning=F, error=FALSE, message=F}
ccc=c
for (i in 1:length(ccc)) {
  for (k in 1:(length(ccc[[1]]$year)-3)) {

  ccc[[i]]$volsumc[k]=sum(ccc[[i]]$vol.sum.c[1:k])
  
    
}}

cccc=do.call(rbind.data.frame,ccc)
cccc=cccc[,-c(9:12)]
cccc=cccc%>%dplyr::rename(vol.sum.c=volsumc,year.1=year)
```


```{r,include=F,warning=F, error=FALSE, message=F}
e=do.call(rbind.data.frame,hh)
e=e[,-c(9:11)]
data_e=e%>%dplyr::rename(year.1=year,Tm=Tmh,d.strss=d.strssm)

data_ee=merge(data_e,cccc)
```





```{r groups}
#Groups and types for the H10

groups <- c('Common_carp', 
            'Pike_perch', 
            'Roach',
            'Tench', 
            'Roach_juv', 
            'Tench_juv', 
            'Macroinvertebrate', 
            'Zooplancton', 
            'Phytoplancton',
            'Detritus')

types  <- c(rep(0, 8), 1, 2)
stgroups <- c(rep(0, 10))

REco.params <- create.rpath.params(group = groups, type = types,stgroup=stgroups)
```




REco.params now contains a list of 4 objects: model, diet, stanzas, and pedigree.
The majority of the parameters are populated with NA save those that have logical
default vaules (i.e 0.66667 for VBGF_d).  

### Model parameters
 

```{r blank modfile table, echo=FALSE, results='asis'}
knitr::kable(REco.params$model, caption = 'Example of the model list created using the 
             `create.rpath.param` function')
```


Note the use of the operator ':=' to assign values.  This is unique to data tables.
Eg: REco.params$model[Group %in% c('Seals', 'Megabenthos'), EE := 0.8]

```{r Model Table partial, echo = F}
knitr::kable(REco.params$model[, list(Group, Type, Biomass, EE)], 
             caption = 'Example of assigning a specific slot or a whole column')

```

Here are the rest of the columns for the model list.
```{r Model Table sans stanzas}
#Model
## Biomass
biomass <- c(1.44,
             0.56,
             1.34,
             0.93,
             0.45,
             0.16,
             0.25,
             0.54,
             1.92,
             48.81)

## Production by biomass

pb <- c(1.69,
        1.52,
        0.71,
        0.48,
        2.00,
        2.00,
        14.50,
        92.43,
        118.7,
        NA)

## Consumption by biomass

qb <- c(4.93,
        2.19,
        5.09,
        5.18,
        5.29,
        5.14,
        48.33,
        308.1,
        rep(NA,2))
```


```{r Model Table sans stanzas}
REco.params$model[, Biomass := biomass]
REco.params$model[, PB := pb]
REco.params$model[, QB := qb]
```



```{r}
# #Fisheries
# #Landings
# fleet <- c(rep(NA, 11))
# REco.params$model[, Fleet := fleet]
# 
# #Discards
# 
# fleet.d <- c(rep(NA, 11))
# REco.params$model[, Fleet.disc := fleet.d]
```

```{r Model Table sans stanzas}
#Biomass accumulation 
REco.params$model[, BioAcc  := c(2.28,0.83,0.93,0.43,rep(0, 6))]

# Unassimilated consumption
REco.params$model[, Unassim := c(rep(0.2, 6), rep(0.4, 2), rep(0, 2))]

#Detrital Fate
REco.params$model[, Detritus := c(rep(1, 9), rep(1, 1))]
# REco.params$model[, Discards := c(rep(0,10))]
# 
# #Fisheries
# #Landings
# trawl  <- c(rep(0, 4), 0.08, 0, 0.32, 0, 0.09, 0, 0.05, 0.2, rep(0, 10), rep(NA, 3))
# mid    <- c(rep(0, 12), 0.3, 0.08, 0.02, rep(0, 7), rep(NA, 3))
# dredge <- c(rep(0, 15), 0.1, 0.5, rep(0, 5), rep(NA, 3))
# REco.params$model[, Trawlers := trawl]
# REco.params$model[, Midwater := mid]
# REco.params$model[, Dredgers := dredge]
# 
# #Discards
# trawl.d  <- c(1e-5, 1e-7, 0.001, 0.001, 0.005, 0.001, 0.009, 0.001, 0.04, 0.001,
#               0.01, 0.08, 0.001, 0.001, 0.001, rep(0, 7), rep(NA, 3))
# mid.d    <- c(rep(0, 2), 0.001, 0.001, 0.01, 0.001, 0.01, rep(0, 4), 0.05, 0.05,
#               0.01, 0.01, rep(0, 7), rep(NA, 3))
# dredge.d <- c(rep(0, 3), 0.001, 0.05, 0.001, 0.05, 0.001, 0.05, 0.001, 0.01, 0.05,
#               rep(0, 3), 0.09, 0.01, 1e-4, rep(0, 4), rep(NA, 3))
# REco.params$model[, Trawlers.disc := trawl.d]
# REco.params$model[, Midwater.disc := mid.d]
# REco.params$model[, Dredgers.disc := dredge.d]
```

```{r Model Table final, echo = F}
knitr::kable(REco.params$model, 
             caption = 'Example of completed model list')

```

###Stanza Parameters




###Diet Parameters

Note : 
eg: REco.params$diet[Group == 'OtherGroundfish', Seabirds := 0.1]
knitr::kable(REco.params$diet[, list(Group, Seabirds, Whales)])
NA: import

Here is the completed model parameter file for R Ecosystem:

```{r diet fill}

REco.params$diet[, Common_carp       := c(NA,NA,NA,NA, 0.01, 0.01, 0.18, 0.22,0.12,0.46,NA)]
                 
REco.params$diet[, Pike_perch        := c(NA,NA,NA,NA, 0.28, 0.02, 0.12, 0.56,NA,0.02,NA)]
 
REco.params$diet[, Roach             := c(NA,NA,NA,NA,NA,NA, 0.02, 0.25,0.14,0.59,NA)]

REco.params$diet[, Tench             := c(NA,NA,NA,NA,NA,NA, 0.22, 0.12,0.10,0.56,NA)]

REco.params$diet[, Roach_juv         := c(NA,NA,NA,NA,NA,NA, 0.01, 0.20,0.39,0.40,NA)]

REco.params$diet[, Tench_juv         := c(NA,NA,NA,NA,NA,NA, 0.01, 0.15,0.24,0.60,NA)]

REco.params$diet[, Macroinvertebrate := c(NA,NA,NA,NA,NA,NA, 0.08, 0.16,0.35,0.41,NA)]

REco.params$diet[, Zooplancton     := c(NA,NA,NA,NA,NA,NA, NA, 0.11,0.27,0.62,NA)]


```
```{r Dietfile Table, echo = F}
knitr::kable(REco.params$diet, caption = 'Diet parameters for R Ecosystem')
```

```{r}
colSums(REco.params$diet[,2:length(REco.params$diet)],na.rm = T)


```



###Pedigree parameters
Rpath does not currently use pedigrees however, future Rpath extensions will use
them.  Therefore we include them in the current parameter object. The
default values are 1 (low confidence).  These defaults are not changed for R
Ecosystem but can obviously be changed in a similar manner to the other parameter
files.
```{r pedigree table, echo = F}
knitr::kable(REco.params$pedigree, caption = 'Pedigree parameters for R Ecosystem')
```

## Running Ecopath


After creating the parameter object, running ecopath in R is relatively 
straightforward.  It is just the function `rpath` supplied with the parameter object.
Additionally, you can supply an ecosystem name for the output.

```{r Running ecopath}
REco <- rpath(REco.params, eco.name = 'R Ecosystem')
REco
```

The output object from `rpath` is an S3 object type called 'Rpath'.  Rpath objects
are a list of parameters from the mass balance.  However, the `print` function will
display the same information as the "Basic Estimates" tab from EwE. You will also 
notice that the `print` function will display whether the model is balanced or not.
If the model was not balanced, it would list the groups that are not balanced.

You can also display the mortalities associated with each group by supplying the
argument `morts = T` to the `print` function.

```{r Ecopath morts}
print(REco, morts = T)
```

Note that if you wish to save the `print` output you need to use the function
`write.rpath`.  This function will also accept the argument 'morts = T'.

The generic function `summary` will display some summary statistics on the model
as well as a list of attributes you can access.  To access any of the other 
attributes simply use the standard list notation.

```{r Ecopath summaries}
summary(REco)
REco$TL
```

One of the advantages of R is its graphical ability.  Users can feel free to develop
their own graphical routines for the Rpath outputs.  However, we have included
a basic food web plot.  The routine can include fisheries, display group numbers or 
names, and even highlight a particular group.

```{r Food Web Plots, fig.align = 'center', fig.height = 7, fig.width = 7}
webplot(REco)
webplot(REco, labels = T)
# webplot(REco, fleets = T, highlight = 'AduRoundfish1')
```





# Calcul

```{r}
# for (i in 1:length(scenarios)) {
#  list_comb.d[[i]]=rbind(list_comb.d[[i]],data_ini.juv)
# }
```

```{r}
# For adult group

list_comb.d[[1]]$WT_Stk=list_comb.d[[1]]$prc_scn/100*list_comb.d[[1]]$Stocking_Tot #Calcul initial biomass by percentage in sceanrio (Stocking total fix)

list_comb.d[[1]]$Nb_Stk=list_comb.d[[1]]$WT_Stk/list_comb.d[[1]]$Wi_Stk #Calcul initial number of species

list_comb.d[[1]]$Wf_F=list_comb.d[[1]]$Wi_Stk*exp((list_comb.d[[1]]$SGR*list_comb.d[[1]]$Duration)/100)   #Calcul final Weight mean by SGR and duration (= 270 day)

list_comb.d[[1]]$Nb_F=(1-list_comb.d[[1]]$Mortality/100)*list_comb.d[[1]]$Nb_Stk #Calcul final number by mortality rate

list_comb.d[[1]]$WT_F=list_comb.d[[1]]$Nb_F*list_comb.d[[1]]$Wf_F #Calcul final biomass
```


```{r}
# For juvenil group

list_comb.d[[1]]$Wf_F[5]=4.30 #Fix initial weight of Roach_juv 
list_comb.d[[1]]$Wf_F[6]=5.60 #Fix initial weight of Tench_juv 

list_comb.d[[1]]$Nb_F[5]=list_comb.d[[1]]$Nb_Stk[3]*72 # #Calcul final number of Roach-juv by multiplying the number of adults by 72 (fix including mortality ) 
list_comb.d[[1]]$Nb_F[6]=list_comb.d[[1]]$Nb_Stk[4]*108 # #Calcul final number of Tench-juv by multiplying the number of adults by 108 (fix including mortality ) 

list_comb.d[[1]]$WT_F[5]=list_comb.d[[1]]$Wf_F[5]*list_comb.d[[1]]$Nb_F[5] #Calcul final biomass of Roach_juv 
list_comb.d[[1]]$WT_F[6]=list_comb.d[[1]]$Wf_F[6]*list_comb.d[[1]]$Nb_F[6]   #Calcul final biomass of Tench_juv
```


```{r}
list_comb.d[[1]]$Prc_F=list_comb.d[[1]]$WT_F/sum(list_comb.d[[1]]$WT_F)*100 #Calcul final percentage by species

list_comb.d[[1]]$Rdt.net=((list_comb.d[[1]]$WT_F-list_comb.d[[1]]$WT_Stk)/1000)/0.1 # Yield net kg/ha (by pond surface 0.1 ha)
```


```{r}
# Duplicate the scenario name
list_comb.d[[1]]$scenario[c(5:6)]=list_comb.d[[1]]$scenario[1]
```


```{r}
list_comb.d[[1]]$Z=-(log(list_comb.d[[1]]$Nb_F/list_comb.d[[1]]$Nb_Stk))#Calcul Z

list_comb.d[[1]]$Nb.mean=(list_comb.d[[1]]$Nb_Stk-list_comb.d[[1]]$Nb_F)/list_comb.d[[1]]$Z#Calcul mean number

list_comb.d[[1]]$W.mean=(list_comb.d[[1]]$Wi_Stk+list_comb.d[[1]]$Wf_F)/2 #Calcul mean weight

# Calcul mean biomass for adult group
list_comb.d[[1]]$B.g=list_comb.d[[1]]$Nb.mean*list_comb.d[[1]]$W.mean
# Calcul mean biomass for juvenil group
list_comb.d[[1]]$B.g[5]=list_comb.d[[1]]$WT_F[5]/2 #Calcul mean biomass of Roach_juv 
list_comb.d[[1]]$B.g[6]=list_comb.d[[1]]$WT_F[6]/2 #Calcul mean biomass of Tench_juv


list_comb.d[[1]]$B.g.m2=list_comb.d[[1]]$B.g/1000 #Calcul mean biomass in g/m2

list_comb.d[[1]]$B_DW=list_comb.d[[1]]$B.g.m2*list_comb.d[[1]]$DW_rate #Calcul mean biomass in dry weight

list_comb.d[[1]]$BA.g=list_comb.d[[1]]$WT_F-list_comb.d[[1]]$WT_Stk #Calcul biomass accumulation

#Calcul P:B for adult group
list_comb.d[[1]]$`P/B`=list_comb.d[[1]]$BA.g/list_comb.d[[1]]$B.g+list_comb.d[[1]]$Z

#Calcul P:B for juv group
list_comb.d[[1]]$`P/B`[5]=list_comb.d[[1]]$BA.g[5]/list_comb.d[[1]]$B.g[5]
list_comb.d[[1]]$`P/B`[6]=list_comb.d[[1]]$BA.g[6]/list_comb.d[[1]]$B.g[6]

list_comb.d[[1]]$Bacc.g.m2=list_comb.d[[1]]$BA.g/1000 # Calcul Biomass acc in g/m2

# Calcul Biomass accumulate in dry weight
list_comb.d[[1]]$Baacc_DW=list_comb.d[[1]]$Bacc.g.m2*list_comb.d[[1]]$DW_rate

```


```{r}
# Add resource group
for (i in 1:length(scenarios)) {
 list_comb.d[[i]]=rbind(list_comb.d[[i]],data_ini.Rgroup)
}
```


```{r}
# Put in dataframe

All_data=do.call(rbind.data.frame,list_comb.d)
```



