---
title: "Simulation scenarios (Polyculture of striped catfish *Pangasianodon hypophthalmus*)"
author: "Ralien R.Purco"
date: "`r Sys.Date()`"
output:
  html_document: default
  word_document: default
  pdf_document: default

knit: |
  (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_format = "all")
  })
---

# Fish species selected

- Striped catfish (*Pangasianodon hypophthalmus*)
- Silver Carp (*Hypophthalmichthys molitrix*)
- *Clarias macrocephalus*
- Common carp (*Cyprinus carpio*)


# Zootechnical performance for each fish species (Use and refer to the  template "Stocking_Hypothesis_ad")

- Number stocked (Nb_Stk)
- Initial weight (Wi_Stk): [insert value]
- Total stocking weight (WT_Stk)
- Stocking total biomass of all fish (Stocking_Tot): [insert value]
- Percent stocked (Prc_Stk)
- Final number (Nb_F)
- Final weight (Wf_F)
- Total final weight (WT_F)
- Percent final (Prc_F)
- Duration: [insert value]
- Specific growth rate (SGR): [insert value]
- Mortality: [insert value]
- Net yield (Rdt.net)
- Unit price (Price.U): [insert value]
- Profit (Profi)
- Natural mortality: Z
- Mean number (Nb.mean)
- Mean weight (W.mean)
- Biomass (B.g)
- Biomass per m² (B.g.m2)
- Dry weight rate (DW_rate): [insert value]
- Biomass dry weight (B_DW)
- Accumulated biomass BA.g
- Production/Biomass ratio (P/B)
- Accumulated biomass per m² (Bacc.g.m2)
- Accumulated biomass per m² in dry weight (Bacc_DW)
- Consumption/Biomass ratio (C/B): [insert value]
- Detritus input (DetInput): [insert value] (*feed)


# Biomass of stocking: 600 kg/ha (6000g for 100m²)[insert value]


# Pond area: 100m² [insert value]


# Assessment of available resources (Use and refer to the  template "Stocking_Hypothesis_Rgroup")

- Biomass dry weight (B_DW): [insert value]
- Production/Biomass ratio (P/B): [insert value]
- Consumption/Biomass ratio (C/B): [insert value]

NB: Separate file for feed if it is not fixed for each scenario (e.g., 3% of biomass of striped catfish)



# Define scenarios

1 Scenario = 1 Fish combinations with different percentages 

```{r,echo=TRUE,warning = FALSE,message = FALSE}

# remove previously loaded items from the current environment and remove previous graphics.
rm(list=ls())
graphics.off()

# Install and load the package to generate the combinations
library(gtools)

# Define the possible percentages (from 2 to 98 in steps of 2) => [Modify the values according to the chosen percentage steps]
percentages <- seq(2, 98, by = 2)
percentages 
# Generate all possible combinations of percentages => [A, B, C, D correspond to the 4 selected species; modify this according to the number of species]
combinations <- expand.grid(A = percentages, B = percentages, C = percentages, D = percentages) 
combinations
# Filter the combinations for those whose sum is equal to 100
valid_combinations <- combinations[rowSums(combinations) == 100, ]
valid_combinations

valid_combinations <-as.data.frame(valid_combinations)

# Add a scenario column (Add a 'scenario' column with unique identifiers 'scenario1', 'scenario2', ... by generating a sequence from 1 to the number of rows in valid_combinations)
valid_combinations$scenario <- paste0("scenario", seq_len(nrow(valid_combinations)),sep="") 
valid_combinations

library(tidyverse)

# Reshapes the data from wide to long format
valid_combinations=valid_combinations %>%pivot_longer(cols=c(1:4),names_to = "sp_scn", values_to = "prc_scn")
valid_combinations

data.valid_combinations=as.data.frame(valid_combinations)

list_combinations=list()
scenarios<-unique(data.valid_combinations$scenario)

for (i in 1:length(scenarios)) {
 list_combinations[[i]]=subset(data.valid_combinations,scenario==scenarios[i])
}


list_comb=list_combinations

```



# Add data


```{r,echo=TRUE,warning = FALSE,message = FALSE}
# define list of packages in vector
package<-c("readxl")

# define function to load all packages
instal<-function(x){ 
  for(pkg in x){
  instal=require(pkg, character.only = T) # load package x 
}}
instal(package) # load list of packages in vector package

# set working directory

setwd("P:\\Thèse Purco RALIEN\\Rpath_fork\\Rpath_fork\\Readme\\fish_feed")

# Import data

data_ini.ad <-read_excel("Stocking_Hypothesis_ad.xlsx",sheet = 1)
data_ini.Feed<-read_excel("Stocking_Hypothesis_Feed.xlsx",sheet = 1)
data_ini.Rgroup<-read_excel("Stocking_Hypothesis_Rgroup.xlsx",sheet = 1)


#add scenario + fish data initial adult
list_comb.d=list()
for (i in 1:length(scenarios)) {
 list_comb.d[[i]]=cbind(data_ini.ad,list_comb[[i]])
}



# Calcul


for (i in 1:length(scenarios)) {


# For adult group

## Calcul initial biomass by percentage in scenario (Stocking total fix)
list_comb.d[[i]]$WT_Stk=list_comb.d[[i]]$prc_scn/100*list_comb.d[[i]]$Stocking_Tot

## Calcul initial number of species
list_comb.d[[i]]$Nb_Stk=list_comb.d[[i]]$WT_Stk/list_comb.d[[i]]$Wi_Stk

## Calcul final Weight mean by SGR and duration
list_comb.d[[i]]$Wf_F=list_comb.d[[i]]$Wi_Stk*exp((list_comb.d[[i]]$SGR*list_comb.d[[i]]$Duration)/100)

## Calcul final number by mortality rate
list_comb.d[[i]]$Nb_F=(1-list_comb.d[[i]]$Mortality/100)*list_comb.d[[i]]$Nb_Stk

## Calcul final biomass
list_comb.d[[i]]$WT_F=list_comb.d[[i]]$Nb_F*list_comb.d[[i]]$Wf_F

## Calcul final percentage by species
list_comb.d[[i]]$Prc_F=list_comb.d[[i]]$WT_F/sum(list_comb.d[[i]]$WT_F)*100

## Yield net kg/ha (by pond surface 0.01 ha) => [ Modify the 0.01 values based on the pond surface area]
list_comb.d[[i]]$Rdt.net=((list_comb.d[[i]]$WT_F-list_comb.d[[i]]$WT_Stk)/1000)/0.01



# Add economic value( Calcul profitability by species)
list_comb.d[[i]]$Profi=list_comb.d[[i]]$Rdt.net*list_comb.d[[i]]$Price.U



# Calcul Z
list_comb.d[[i]]$Z=-(log(list_comb.d[[i]]$Nb_F/list_comb.d[[i]]$Nb_Stk))

# Calcul mean number
list_comb.d[[i]]$Nb.mean=(list_comb.d[[i]]$Nb_Stk-list_comb.d[[i]]$Nb_F)/list_comb.d[[i]]$Z

# Calcul mean weight
list_comb.d[[i]]$W.mean=(list_comb.d[[i]]$Wi_Stk+list_comb.d[[i]]$Wf_F)/2

# Calcul mean biomass for adult group
list_comb.d[[i]]$B.g=list_comb.d[[i]]$Nb.mean*list_comb.d[[i]]$W.mean

# Calcul mean biomass in g/m2 (by pond surface 100m²)
## => [ Modify the 100m² values based on the pond surface area]
list_comb.d[[i]]$B.g.m2=list_comb.d[[i]]$B.g / 100


# Calcul mean biomass in dry weight
list_comb.d[[i]]$B_DW=list_comb.d[[i]]$B.g.m2*list_comb.d[[i]]$DW_rate


# Calcul biomass accumulation
list_comb.d[[i]]$BA.g=list_comb.d[[i]]$WT_F-list_comb.d[[i]]$WT_Stk


# Calcul P:B for adult group
list_comb.d[[i]]$`P/B`=list_comb.d[[i]]$BA.g/list_comb.d[[i]]$B.g+list_comb.d[[i]]$Z

# Calcul Biomass acc in g/m2 (by pond surface 100m²)
## => [ Modify the 100m² values based on the pond surface area]
list_comb.d[[i]]$Bacc.g.m2=list_comb.d[[i]]$BA.g/100

# Calcul Biomass accumulate in dry weight
list_comb.d[[i]]$Baacc_DW=list_comb.d[[i]]$Bacc.g.m2*list_comb.d[[i]]$DW_rate

}



# Add scenario + data feed
## [c(5:5)=> modify based on the feed row]

for (i in 1:length(scenarios)) {
 list_comb.d[[i]]=rbind(list_comb.d[[i]],data_ini.Feed)
 list_comb.d[[i]]$scenario[c(5:5)]=list_comb.d[[i]]$scenario[1]
}



for (i in 1:length(scenarios)) {

# For Feed group
## Calcul biomass => Calculate the biomass of feed by multiplying the initial number of striped catfish by 251 (factor including growth) [251 => insert value based on simulation]. Adjust this value to the surface area per m² by dividing by 100 [100m² => insert value based on the pond surface area], then convert it to dry weight. Calculate the average by dividing by the duration.
## [[5]=> modify based on the feed row]
list_comb.d[[i]]$B_DW[5]=list_comb.d[[i]]$Nb_Stk[1]*251/100*list_comb.d[[i]]$DW_rate[5]/list_comb.d[[i]]$Duration[5]

## Calcul DetInput
## Calculate the Detritus input of feed by multiplying the biomass of feed by the duration, then calculate the average by dividing by 2.
## [[5]=> modify based on the feed row]
list_comb.d[[i]]$DetInput[5]=list_comb.d[[i]]$B_DW[5]*list_comb.d[[i]]$Duration[5]/2

}



for (i in 1:length(scenarios)) {
# Add economic value - feed value
## Calculate the profitability by substracting the fish profitability by the feed value ( which obtained by multiplying the initial number of striped catfish by 251 (factor including growth) [251 => insert value based on simulation].Dividing by 1000 to have the value in kg. Adjust this value to the surface area per ha by dividing by 0.0100 [0.01 ha => insert value based on the pond surface area], then multiply it by the price of the feed 0.6) => [ Modify the 0.6 values based on the price of the feed]
## [[1]=> modify based on the feed fish row]
list_comb.d[[i]]$Profi[1]=list_comb.d[[i]]$Profi[1] - ((list_comb.d[[i]]$Nb_Stk[1]*251)/1000)/0.01*0.6

}



# Add resource group
## [c(6:9)=> modify based on the resource available row]
for (i in 1:length(scenarios)) {
 list_comb.d[[i]]=rbind(list_comb.d[[i]],data_ini.Rgroup)
 list_comb.d[[i]]$scenario[c(6:9)]=list_comb.d[[i]]$scenario[1]
}


# Loop to reorganize the rows of each dataframe in the list list_comb.d (feed and detritus at the end )
for (i in 1:length(list_comb.d)) {

  # Extract the current dataframe
  df <- list_comb.d[[i]]

  # Check if the dataframe has at least 8 rows
  if (nrow(df) >= 8) {
    # Extract the 5th row
    ligne_5 <- df[5, ]

    # Remove the 5th row from the original dataframe
    df <- df[-5, ]

    # Insert the 5th row at the 8th position
    df <- rbind(df[1:7, ], ligne_5, df[8:nrow(df), ])
  }

  # Update the dataframe in the list
  list_comb.d[[i]] <- df
}

list_comb.d.all=list_comb.d

# Put in dataframe

All_data=do.call(rbind.data.frame,list_comb.d.all)



# Ecopath for all scenario


# Install package
# remotes::install_github('https://github.com/Purco/Rpath_fork.git')
# remotes::install_github('https://github.com/Purco/enaR.git')


# Run package
library(Rpath); library(data.table)

temps_debut <- system.time({

# start
results_list <- list()
for (i in 1:length(scenarios)) {

# Groups and types for each functional group
## => [Modify and reorder  the functional group according to "list_comb.d"]
groups <- c('Striped_catfish',
            'Silver_Carp',
            'Clarias_macrocephalus',
            'Common_carp',
            'MIB',
            'Zooplankton',
            'Phytoplankton',
            'Feed',
            'Detritus')

## => [Modify and reorder  the functional group according to "list_comb.d"]
## => [0 for consumer, 1 for primary production, 2 for detritus and feed]
types  <- c(rep(0, 6), 1,2, 2)

## [9 => modify based on the total number of functional groups]
stgroups <- c(rep(0, 9))

REco.params <- create.rpath.params(group = groups, type = types,stgroup=stgroups)

REco.params$model[, Biomass := All_data[All_data$scenario==scenarios[i],]$B_DW]

REco.params$model[, PB := All_data[All_data$scenario==scenarios[i],]$`P/B`]

REco.params$model[, QB := All_data[All_data$scenario==scenarios[i],]$`C/B`]


#Biomass accumulation
## [ => c(1:4) represents the fish groups;(0, 5) for other functional groups]
REco.params$model[, BioAcc  := c(All_data[All_data$scenario==scenarios[i],]$Baacc_DW[c(1:4)],rep(0, 5))]

# Unassimilated consumption
## [rep(0.2, 4) => for the fish groups;rep(0.4, 2) for MIB and Zoo; rep(0, 3) for other functional groups]
REco.params$model[, Unassim := c(rep(0.2, 4), rep(0.4, 2), rep(0, 3))]

# Detritus import
## Add value from feed
REco.params$model[, DetInput := All_data[All_data$scenario==scenarios[i],]$DetInput]

#Detrital Fate
REco.params$model[, Detritus := c(rep(1, 7), rep(1, 2))]

## Add second detrital Fate for feed
REco.params$model[, Feed := c(rep(0, 7),1,0)]



# Diet

REco.params$diet[, Striped_catfish       := c(NA,NA,NA,NA, 0.015, 0.025, 0.005, 0.95,0.005,NA)]

REco.params$diet[, Silver_Carp           := c(NA,NA,NA,NA, 0.00, 0.10, 0.80, 0.00,0.10,NA)]

REco.params$diet[, Clarias_macrocephalus := c(NA,NA,NA,NA, 0.45, 0.35, 0.10, 0.00,0.10,NA)]

REco.params$diet[, Common_carp           := c(NA,NA,NA,NA, 0.20, 0.20, 0.00, 0.40,0.20,NA)]

REco.params$diet[, MIB                   := c(NA,NA,NA,NA, 0.10, 0.20, 0.20, 0.00,0.50,NA)]

REco.params$diet[, Zooplankton           := c(NA,NA,NA,NA, 0.00, 0.10, 0.60, 0.00,0.30,NA)]

REco <- rpath(REco.params, eco.name = 'R Ecosystem')
## [9 => modify based on the total number of functional groups]
results_list[[i]]=cbind(data.frame(REco[c(4:13,15)]),data.frame(Scena = rep(scenarios[i], 9)))
}

All_results=do.call(rbind.data.frame,results_list)

All_results_sc=cbind(All_results,All_data)

# end
})
temps_ecoule <- temps_debut["elapsed"]
print(temps_ecoule)



# EnaR



temps_debut <- system.time({

# start
res.enaR_list <- list()
for (k in 1:length(scenarios)) {

# Steps of Rpath to enaR (network) conversion:
# Set up: pull in group names, count number of living vs. non-living groups
groups <- as.vector(REco$Group)
nliving <- nrow(REco.params$model[Type <  2, ])
ndead   <- nrow(REco.params$model[Type == 2, ])


# Calculate consumption values from diet matrix: DC*QB*Biomass

diet<-REco$DC
QQ<-matrix(nrow = (nliving + ndead + 1),ncol=nliving)
for (j in 1:nliving){
QQ[,j]<-diet[,j]*results_list[[k]]$QB[j]*results_list[[k]]$Biomass[j]
}

# Ignore imports in diet matrix
QQ<-QQ[1:(nliving+ndead),]#change (PR)

# Name the consumption matrix
colnames(QQ)<-groups[1:nliving]
rownames(QQ)<-groups[1:(nliving+ndead)]#change (PR)
# <Deal with discards>

# Calculate flow to detritus (first need to calculate M0 values for each node), append to diet matrix
M0<-results_list[[k]]$PB*(1-results_list[[k]]$EE)

Detritus<-(M0*results_list[[k]]$Biomass+results_list[[k]]$QB*results_list[[k]]$Biomass*results_list[[k]]$Unassim)*REco$DetFate[,ndead]#change (PR)

## Add if there is feed
Feed<-(M0*REco$Biomass+REco$QB*REco$Biomass*REco$Unassim)*REco$DetFate[,1]#Add (PR)

Detritus[(nliving+ndead)]<-0 #change (PR)

## Add if there is feed
Feed[(nliving+1)]<-0 #Add (PR)

QQ<-cbind(QQ,Feed,Detritus)#change (PR)

# Calculate exports: catch, positive biomass accumulation, detrital production
Export<-(ifelse(results_list[[k]]$BA>0,results_list[[k]]$BA,0))
Export<-Export[1:(nliving+ndead)]

# for (i in 1:ndead){
#   Export[nliving+i]<-REco$PB[(nliving+i)]*REco$Biomass[(nliving+i)]
# } # Modified

for (i in 1:ndead){
  Export[nliving+i]<-M0[(nliving+i)]*results_list[[k]]$Biomass[(nliving+i)]-sum(Export[1:nliving])
}


# Calculate respiration, assuming detrital groups have 0 respiration
Resp<-((1-results_list[[k]]$Unassim)*results_list[[k]]$QB-results_list[[k]]$PB)*results_list[[k]]$Biomass
Resp<-ifelse(Resp>0,Resp,0)
Resp<-Resp[1:(nliving+ndead)]

Resp[(nliving+ndead):(nliving+ndead)]<-0 #change (PR)


# Estimate respiration of primary producers

gross<-0

## [c(7) =>  c(7) represents the primary production row; adjust this column according to the corresponding row in the data]
Resp[c(7)]<-0

# Calculate imports: negative biomass accumulation, grosspp

Import<-abs(ifelse(results_list[[k]]$BA<0,results_list[[k]]$BA,0))
# Import<- REco$PB*REco$Biomass

## [c(7) =>  c(7) represents the primary production row; adjust this column according to the corresponding row in the data]
Import[c(7)]<-gross
Import<-Import[1:(nliving+ndead)]

# Assign biomass values
Biomass<-results_list[[k]]$Biomass[1:(nliving+ndead)]

# Pack the model

# install.packages("gdata", repos = "https://packagemanager.posit.co/cran/2023-05-06")
# update.packages(ask = FALSE)

# remotes::install_github('Purco/enaR')

library(enaR)



orig.network<-enaR::pack(flow = QQ,
                        input = Import,
                        export = Export,
                        living = c(rep(TRUE,nliving),rep(FALSE,ndead)),
                        respiration = Resp,
                        storage = Biomass)

res.enaR_list[[k]]=merge(results_list[[k]],data.frame(t(enaFlow(orig.network)$ns[,c(2,3,5)])))
}

All_enar.res=do.call(rbind.data.frame,res.enaR_list)

All_enar.res_sc=cbind(All_enar.res,All_data)

# end
})
temps_ecoule <- temps_debut["elapsed"]
print(temps_ecoule)

#print result
All_enar.res_sc
write.csv(All_enar.res_sc,"All_enar_res_simul.csv")
```





# Visualisation des resultats

```{r,echo=FALSE,warning = FALSE,message = FALSE}
library(stringr)
All_enar.res_sc$scena1 <- str_extract(All_enar.res_sc$Scena, "\\d+$")
```

## Number of scenario
```{r,echo=FALSE,warning = FALSE,message = FALSE}

length(unique(All_enar.res_sc$scena1))
```


## Summary

```{r,echo=FALSE,warning = FALSE,message = FALSE}
Rdt.All_enar.res_sc=All_enar.res_sc%>%group_by(scenario,scena1)%>% summarise(RDT=sum(Rdt.net,na.rm = T),FCI=mean(FCI),Profitability=sum(Profi,na.rm = T),n=n())
Rdt.All_enar.res_sc

# Reorganize and display according to the scenario number
All_enar.res_sc_ord <- All_enar.res_sc %>%
  group_by(scenario, scena1) %>%
  summarise(
    RDT = sum(Rdt.net, na.rm = TRUE),
    FCI = mean(FCI),
    Profitability = sum(Profi, na.rm = TRUE),
    n = n(),
    .groups = "drop"
  ) %>%
  mutate(scena1_num = as.numeric(gsub("\\D", "", scena1))) %>%  # extrait les chiffres
  arrange(scena1_num)


summary_stats <- All_enar.res_sc_ord %>%
  summarise(
    RDT_min = min(RDT, na.rm = TRUE),
    RDT_max = max(RDT, na.rm = TRUE),
    RDT_mean = mean(RDT, na.rm = TRUE),
    RDT_sd = sd(RDT, na.rm = TRUE),

    FCI_min = min(FCI, na.rm = TRUE),
    FCI_max = max(FCI, na.rm = TRUE),
    FCI_mean = mean(FCI, na.rm = TRUE),
    FCI_sd = sd(FCI, na.rm = TRUE),

    Profit_min = min(Profitability, na.rm = TRUE),
    Profit_max = max(Profitability, na.rm = TRUE),
    Profit_mean = mean(Profitability, na.rm = TRUE),
    Profit_sd = sd(Profitability, na.rm = TRUE)
  )
summary_stats
```


### Summary

```{r,echo=FALSE,warning = FALSE,message = FALSE,fig.width=7,fig.height=2}
library(dplyr)

# Filtrer les groupes et calculer les statistiques
data_EEAll1 <- All_enar.res_sc %>%
  filter(Group %in% c("MIB", "Zooplankton", "Phytoplankton", "Detritus", "Feed")) %>%
  group_by(Group) %>%
  summarise(
    Minimum = min(EE, na.rm = TRUE),
    Maximum = max(EE, na.rm = TRUE),
    Moyenne = mean(EE, na.rm = TRUE),
    CV = sd(EE, na.rm = TRUE) / mean(EE, na.rm = TRUE)
  )
data_EEAll1
```




## Net yield
```{r,echo=FALSE,warning = FALSE,message = FALSE}
Rdt.All_enar.res_sc=All_enar.res_sc%>%group_by(scenario,scena1)%>% summarise(RDT=sum(Rdt.net,na.rm = T),FCI=mean(FCI),Profitability=sum(Profi,na.rm = T),n=n())
Rdt.All_enar.res_sc

# Reorganize and display according to the scenario number
All_enar.res_sc_ord <- All_enar.res_sc %>%
  group_by(scenario, scena1) %>%
  summarise(
    RDT = sum(Rdt.net, na.rm = TRUE),
    FCI = mean(FCI),
    Profitability = sum(Profi, na.rm = TRUE),
    n = n(),
    .groups = "drop"
  ) %>%
  mutate(scena1_num = as.numeric(gsub("\\D", "", scena1))) %>%  # extrait les chiffres
  arrange(scena1_num)

```



### Plot
```{r,echo=FALSE,warning = FALSE,message = FALSE}
## Plot : Ordre 1-> 18424

All_enar.res_sc_ord <- All_enar.res_sc_ord %>%
  mutate(scena1_num = factor(scena1_num, levels = as.character(1:18424)))

ggplot(All_enar.res_sc_ord,aes(x =scena1_num,y=RDT))+
  geom_point()+
  theme_bw() +
  theme(
    axis.line = element_line(colour = "black"),
    legend.key = element_blank(),
    panel.background = element_rect(fill = NA),
    panel.grid = element_blank(),
    panel.spacing = unit(0.1, "lines"),
    strip.text = element_text(color="black",size = 12),
    axis.text = element_text(color="black",size = 13),
    # axis.text.x = element_text(color="black",size = 13,angle=30,hjust=1),
    axis.title = element_text(color="black",size = 16,face="bold"),
    legend.title = element_text(color="black",size = 14,face="bold"),
    legend.text = element_text(color="black",size = 13,face="bold")
      )+
  labs(x="Scenarios: 1 \u2192 18424",y="Net yield (kg/ha)")
```


## Profitability


### Plot

```{r,echo=FALSE,warning = FALSE,message = FALSE}

ggplot(All_enar.res_sc_ord,aes(x =scena1_num,y=Profitability))+
  geom_point()+
  theme_bw() +
  theme(
    axis.line = element_line(colour = "black"),
    legend.key = element_blank(),
    panel.background = element_rect(fill = NA),
    panel.grid = element_blank(),
    panel.spacing = unit(0.1, "lines"),
    strip.text = element_text(color="black",size = 12),
    axis.text = element_text(color="black",size = 13),
    # axis.text.x = element_text(color="black",size = 13,angle=30,hjust=1),
    axis.title = element_text(color="black",size = 16,face="bold"),
    legend.title = element_text(color="black",size = 14,face="bold"),
    legend.text = element_text(color="black",size = 13,face="bold")
      )+
  labs(x="Scenarios: 1 \u2192 18424",y="Profitability ($/ha)")
```


## Finn cycling index (FCI)


### Plot

```{r,echo=FALSE,warning = FALSE,message = FALSE}

ggplot(All_enar.res_sc_ord,aes(x =scena1_num,y=FCI*100))+
  geom_point()+
  theme_bw() +
  theme(
    axis.line = element_line(colour = "black"),
    legend.key = element_blank(),
    panel.background = element_rect(fill = NA),
    panel.grid = element_blank(),
    panel.spacing = unit(0.1, "lines"),
    strip.text = element_text(color="black",size = 12),
    axis.text = element_text(color="black",size = 13),
    # axis.text.x = element_text(color="black",size = 13,angle=30,hjust=1),
    axis.title = element_text(color="black",size = 16,face="bold"),
    legend.title = element_text(color="black",size = 14,face="bold"),
    legend.text = element_text(color="black",size = 13,face="bold")
      )+
  labs(x="Scenarios: 1 \u2192 18424",y="Finn cycling index (%)")
```

## Ecotrophic efficiency 


### Boxplot for all available resources

```{r,echo=FALSE,warning = FALSE,message = FALSE,fig.width=14}
ggplot(All_enar.res_sc[All_enar.res_sc$Group%in%c("MIB","Zooplankton","Phytoplankton","Feed","Detritus"),], aes(x=EE, y=Group)) +
  geom_boxplot() +
  scale_x_continuous(breaks = function(x) seq(floor(min(x)), ceiling(max(x)), by = 0.5))+
  stat_boxplot(geom="errorbar",width=0.5, coef=NULL)+
  stat_summary(fun.y=mean, geom="point", shape=20, size=2, color="red", fill="red") +
  theme_bw() +
  theme(
   axis.line = element_line(colour = "black"),
    legend.key = element_blank(),
    panel.background = element_rect(fill = NA),
    panel.grid = element_blank(),
    panel.spacing = unit(0.1, "lines"),
    strip.text = element_text(color="black",size = 12),
    axis.text = element_text(color="black",size = 13),
    axis.title = element_text(color="black",size = 16,face="bold"),
    legend.title = element_text(color="black",size = 14,face="bold"),
    legend.text = element_text(color="black",size = 13,face="bold")
      )+
  labs(y="Group",x="Ecotrophic efficiency")
```



### Macroinvertebrate

```{r,echo=FALSE,warning = FALSE,message = FALSE}
All_enar.res_sc <- All_enar.res_sc %>%
  mutate(scena2 = factor(ceiling(row_number() / 9), levels = 1:18424))
ggplot(All_enar.res_sc[All_enar.res_sc$Group=="MIB",],aes(x =scena2,y=EE))+
  geom_point()+
  theme_bw() +
  theme(
    axis.line = element_line(colour = "black"),
    legend.key = element_blank(),
    panel.background = element_rect(fill = NA),
    # panel.grid.major = element_line(colour = "grey75",size=0.5),
    # panel.grid.minor = element_line(colour = "grey75",size=0.2),
     panel.grid = element_blank(),
    panel.spacing = unit(0.1, "lines"),
    strip.text = element_text(color="black",size = 12),
    axis.text = element_text(color="black",size = 13),
    # axis.text.x = element_text(color="black",size = 13,angle=30,hjust=1),
    axis.title = element_text(color="black",size = 16,face="bold"),
    legend.title = element_text(color="black",size = 14,face="bold"),
    legend.text = element_text(color="black",size = 13,face="bold")
      )+
  labs(x="Scenarios: 1 \u2192 18424",y="EE_Macroinvertebrate")
```


### Zooplankton


```{r,echo=FALSE,warning = FALSE,message = FALSE}
ggplot(All_enar.res_sc[All_enar.res_sc$Group=="Zooplankton",],aes(x =scena2,y=EE))+
  geom_point()+
  theme_bw() +
  theme(
    axis.line = element_line(colour = "black"),
    legend.key = element_blank(),
    panel.background = element_rect(fill = NA),
   panel.grid = element_blank(),
    panel.spacing = unit(0.1, "lines"),
    strip.text = element_text(color="black",size = 12),
    axis.text = element_text(color="black",size = 13),
    # axis.text.x = element_text(color="black",size = 13,angle=30,hjust=1),
    axis.title = element_text(color="black",size = 16,face="bold"),
    legend.title = element_text(color="black",size = 14,face="bold"),
    legend.text = element_text(color="black",size = 13,face="bold")
      )+
  labs(x="Scenarios: 1 \u2192 18424",y="EE_Zooplancton")

```



### Phytoplankton

```{r,echo=FALSE,warning = FALSE,message = FALSE}
ggplot(All_enar.res_sc[All_enar.res_sc$Group=="Phytoplankton",],aes(x =scena2,y=EE))+
  geom_point()+
  theme_bw() +
  theme(
    axis.line = element_line(colour = "black"),
    legend.key = element_blank(),
    panel.background = element_rect(fill = NA),
    # panel.grid.major = element_line(colour = "grey75",size=0.5),
    # panel.grid.minor = element_line(colour = "grey75",size=0.2),
     panel.grid = element_blank(),
    panel.spacing = unit(0.1, "lines"),
    strip.text = element_text(color="black",size = 12),
    axis.text = element_text(color="black",size = 13),
    # axis.text.x = element_text(color="black",size = 13,angle=30,hjust=1),
    axis.title = element_text(color="black",size = 16,face="bold"),
    legend.title = element_text(color="black",size = 14,face="bold"),
    legend.text = element_text(color="black",size = 13,face="bold")
      )+
  labs(x="Scenarios: 1 \u2192 18424",y="EE_Phytoplancton")

```


### Detritus

```{r,echo=FALSE,warning = FALSE,message = FALSE}
ggplot(All_enar.res_sc[All_enar.res_sc$Group=="Detritus",],aes(x =scena2,y=EE))+
  geom_point()+
  theme_bw() +
  theme(
    axis.line = element_line(colour = "black"),
    legend.key = element_blank(),
    panel.background = element_rect(fill = NA),
    # panel.grid.major = element_line(colour = "grey75",size=0.5),
    # panel.grid.minor = element_line(colour = "grey75",size=0.2),
     panel.grid = element_blank(),
    panel.spacing = unit(0.1, "lines"),
    strip.text = element_text(color="black",size = 12),
    axis.text = element_text(color="black",size = 13),
    # axis.text.x = element_text(color="black",size = 13,angle=30,hjust=1),
    axis.title = element_text(color="black",size = 16,face="bold"),
    legend.title = element_text(color="black",size = 14,face="bold"),
    legend.text = element_text(color="black",size = 13,face="bold")
      )+
  labs(x="Scenarios: 1 \u2192 18424",y="EE_Detritus")

```


### Feed

```{r,echo=FALSE,warning = FALSE,message = FALSE}
ggplot(All_enar.res_sc[All_enar.res_sc$Group=="Feed",],aes(x =scena2,y=EE))+
  geom_point()+
  theme_bw() +
  theme(
    axis.line = element_line(colour = "black"),
    legend.key = element_blank(),
    panel.background = element_rect(fill = NA),
    # panel.grid.major = element_line(colour = "grey75",size=0.5),
    # panel.grid.minor = element_line(colour = "grey75",size=0.2),
     panel.grid = element_blank(),
    panel.spacing = unit(0.1, "lines"),
    strip.text = element_text(color="black",size = 12),
    axis.text = element_text(color="black",size = 13),
    # axis.text.x = element_text(color="black",size = 13,angle=30,hjust=1),
    axis.title = element_text(color="black",size = 16,face="bold"),
    legend.title = element_text(color="black",size = 14,face="bold"),
    legend.text = element_text(color="black",size = 13,face="bold")
      )+
  labs(x="Scenarios: 1 \u2192 18424",y="EE_Feed")

```


# Screening scenario 

## Select the fish species with performance indicators (Ecotrophic efficiency, net yield, Finn Cycling Index)

```{r,echo=FALSE,warning = FALSE,message = FALSE}
# Scenario
slct.scn= All_enar.res_sc[!All_enar.res_sc$Group%in%c("MIB","Zooplankton","Phytoplankton","Feed","Detritus"),c(1,48,46,49)] %>% pivot_wider(names_from="Group", values_from="prc_scn")

## rename
slct.scn<- slct.scn %>%
  rename(prc.Striped_catfish = Striped_catfish,
         prc.Silver_Carp = Silver_Carp,
         prc.Clarias_macrocephalus = Clarias_macrocephalus,
         prc.Common_carp = Common_carp)


# EE
slct.EE= All_enar.res_sc[!All_enar.res_sc$Group%in%c("Striped_catfish","Silver_Carp","Clarias_macrocephalus","Common_carp"),c(1,7,46,49)] %>% pivot_wider(names_from="Group", values_from="EE")

## rename
slct.EE<- slct.EE %>%
  rename(EE.Macroinvertebrate = MIB,
         EE.Zooplancton=Zooplankton,
         EE.Phytoplancton=Phytoplankton,
         EE.Feed=Feed,
         EE.Detritus=Detritus)

# Rdt et FCI
Rdt.All_enar.res_sc=All_enar.res_sc%>%group_by(scenario,scena1)%>% summarise(RDT=sum(Rdt.net,na.rm = T),FCI=mean(FCI),Profitability=sum(Profi,na.rm = T),n=n())


# Merge
merge.All_enar.res_sc=merge(slct.scn,slct.EE)
merge.All_enar.res_sc=merge(merge.All_enar.res_sc,Rdt.All_enar.res_sc)

# print result

write.csv(merge.All_enar.res_sc,"merge.All_enar.res_simul.csv")
merge.All_enar.res_sc
```


# Select the best scenario

## Nombre de scenario ayant EE>1.1 [1.1 => insert value]
```{r,echo=FALSE,warning = FALSE,message = FALSE}
# select EE sup ou = 1.1
dat.EE.selct=All_enar.res_sc[All_results_sc$EE > 1.1, ]

# nombre de scenario ayant EE>1.1
EE.sup=unique(dat.EE.selct$scenario)

slct_All_enar.res_sc=All_enar.res_sc[!All_enar.res_sc$scenario%in%c(EE.sup),]

slct_All_enar.res_sc
```


```{r,echo=FALSE,warning = FALSE,message = FALSE}

## [1:2085 => insert value] => length(unique(slct_All_enar.res_sc$scena2))
slct_All_enar.res_sc <- slct_All_enar.res_sc %>%
  mutate(scena2 = factor(ceiling(row_number() / 9), levels = 1:2085))
```







