---
title: "Simulation scenarios (Polyculture of Grass Carp *Ctenopharyngodon idella*)"
author: "Ralien R.Purco"
date: "`r Sys.Date()`"
output:
  html_document: default
  word_document: default
  pdf_document: default
  
knit: |
  (function(inputFile, encoding) {
    rmarkdown::render(inputFile, encoding = encoding, output_format = "all")
  })
---


# Fish species selected

- Grass Carp (*Ctenopharyngodon idella*) 
- Common Carp (*Cyprinus carpio*) 
- Pikeperch (*Sander lucioperca*)  
- Roach (*Rutilus rutilus*)  
- Tench (*Tinca tinca*) 

# Zootechnical performance for each fish species (Use and refer to the  template "Stocking_Hypothesis_ad")

- Number stocked (Nb_Stk)
- Initial weight (Wi_Stk): [insert value]
- Total stocking weight (WT_Stk)
- Stocking total biomass of all fish (Stocking_Tot): [insert value]
- Percent stocked (Prc_Stk)
- Final number (Nb_F)
- Final weight (Wf_F)
- Total final weight (WT_F)
- Percent final (Prc_F)
- Duration: [insert value]
- Specific growth rate (SGR): [insert value]
- Mortality: [insert value]
- Net yield (Rdt.net)
- Unit price (Price.U): [insert value]
- Profit (Profi)
- Natural mortality: Z
- Mean number (Nb.mean)
- Mean weight (W.mean)
- Biomass (B.g)
- Biomass per m² (B.g.m2)
- Dry weight rate (DW_rate): [insert value]
- Biomass dry weight (B_DW)
- Accumulated biomass BA.g
- Production/Biomass ratio (P/B)
- Accumulated biomass per m² (Bacc.g.m2)
- Accumulated biomass per m² in dry weight (Bacc_DW)
- Consumption/Biomass ratio (C/B): [insert value]
- Detritus input (DetInput)



# Biomass of stocking: 153 kg/ha (7650g for 500m²)[insert value]


# Pond area: 500m² [insert value]

# Assessment of juvenile production from the fry of the roah and tench adult (Use and refer to the  template "Stocking_Hypothesis_juv")
- Stocking total biomass of all fish (Stocking_Tot): [insert value]
- Unit price (Price.U): [insert value]
- Consumption/Biomass ratio (C/B): [insert value]

# Assessment of available resources (Use and refer to the  template "Stocking_Hypothesis_Rgroup")

- Biomass dry weight (B_DW): [insert value]
- Production/Biomass ratio (P/B): [insert value]
- Consumption/Biomass ratio (C/B): [insert value]

NB: A separate file was used for feed, and it was fixed for each scenario: 44 485 g for the entire period per pond.




# Define scenarios

```{r,echo=T,warning = FALSE,message = FALSE}
# remove previously loaded items from the current environment and remove previous graphics.
rm(list=ls())
graphics.off()

# Install and load the package to generate the combinations
library(gtools)

# Define the possible percentages (from 5 to 95 in steps of 5) => [Modify the values according to the chosen percentage steps]
percentages <- seq(5, 95, by = 5)

# Generate all possible combinations of percentages => [A, B, C, D, E correspond to the 5 selected species; modify this according to the number of species]
combinations <- expand.grid(A = percentages, B = percentages, C = percentages, D = percentages,E = percentages)

# Filter the combinations for those whose sum is equal to 100
valid_combinations <- combinations[rowSums(combinations) == 100, ]


valid_combinations <-as.data.frame(valid_combinations)

# Add a scenario column
# Add a scenario column (Add a 'scenario' column with unique identifiers 'scenario1', 'scenario2', ... by generating a sequence from 1 to the number of rows in valid_combinations)
valid_combinations$scenario <- paste0("scenario", seq_len(nrow(valid_combinations)),sep="")


library(tidyverse)

valid_combinations=valid_combinations %>%pivot_longer(cols=c(1:5),names_to = "sp_scn", values_to = "prc_scn") # 5 number of species

data.valid_combinations=as.data.frame(valid_combinations)

list_combinations=list()
scenarios<-unique(data.valid_combinations$scenario)

for (i in 1:length(scenarios)) {
 list_combinations[[i]]=subset(data.valid_combinations,scenario==scenarios[i])
}


list_comb=list_combinations

```



# Add data


```{r,echo=T,warning = FALSE,message = FALSE}
# define list of packages in vector
package<-c("readxl")

# define function to load all packages
instal<-function(x){ 
  for(pkg in x){
  instal=require(pkg, character.only = T) # load package x 
}}
instal(package) # load list of packages in vector package


# set working directory
setwd("P:\\Thèse Purco RALIEN\\Rpath_fork\\Rpath_fork\\Readme\\fish_reprod_feed")

# Import data
data_ini.ad<-read_excel("Stocking_Hypothesis_ad.xlsx",sheet = 1)
data_ini.Feed<-read_excel("Stocking_Hypothesis_Feed.xlsx",sheet = 1)
data_ini.juv<-read_excel("Stocking_Hypothesis_juv.xlsx",sheet = 1)
data_ini.Rgroup<-read_excel("Stocking_Hypothesis_Rgroup.xlsx",sheet = 1)

# add scenario + data adult
list_comb.d=list()
for (i in 1:length(scenarios)) {
 list_comb.d[[i]]=cbind(data_ini.ad,list_comb[[i]])
}

# add scenario + data juv
for (i in 1:length(scenarios)) {
 list_comb.d[[i]]=rbind(list_comb.d[[i]],data_ini.juv)
}


# Calcul


for (i in 1:length(scenarios)) {
  

# For adult group
  
## Calcul initial biomass by percentage in sceanrio (Stocking total fix)
list_comb.d[[i]]$WT_Stk=list_comb.d[[i]]$prc_scn/100*list_comb.d[[i]]$Stocking_Tot 

## Calcul initial number of species
list_comb.d[[i]]$Nb_Stk=list_comb.d[[i]]$WT_Stk/list_comb.d[[i]]$Wi_Stk 

## Calcul final Weight mean by SGR and duration 
list_comb.d[[i]]$Wf_F=list_comb.d[[i]]$Wi_Stk*exp((list_comb.d[[i]]$SGR*list_comb.d[[i]]$Duration)/100)

## Calcul final number by mortality rate
list_comb.d[[i]]$Nb_F=(1-list_comb.d[[i]]$Mortality/100)*list_comb.d[[i]]$Nb_Stk 

## Calcul final biomass
list_comb.d[[i]]$WT_F=list_comb.d[[i]]$Nb_F*list_comb.d[[i]]$Wf_F 



# For juvenil group

## Fix initial weight of Roach_juv 
### [[6]=> modify based on the Roach_juv row]
### =5 => Initial weight (Wi_Stk): [insert value]
list_comb.d[[i]]$Wf_F[6]=5 

## Fix initial weight of Tench_juv 
## [[7]=> modify based on the Tench_juv row]
### =1.5 => Initial weight (Wi_Stk): [insert value]
list_comb.d[[i]]$Wf_F[7]=1.5

## Calcul final number of Roach-juv [6] by multiplying the number of adults by 1000 [4](fix including mortality ) 
### minus 3 => -3: there must be at least 3 adults
list_comb.d[[i]]$Nb_F[6]=(list_comb.d[[i]]$Nb_Stk[4]-3)*1000
## Calcul final number of Tench-juv [7] by multiplying the number of adults by 1000 [5] (fix including mortality )
### minus 3 => -3: there must be at least 3 adults
list_comb.d[[i]]$Nb_F[7]=(list_comb.d[[i]]$Nb_Stk[5]-3)*1000

## Calcul final biomass of Roach_juv
list_comb.d[[i]]$WT_F[6]=list_comb.d[[i]]$Wf_F[6]*list_comb.d[[i]]$Nb_F[6]  
## Calcul final biomass of Tench_juv
list_comb.d[[i]]$WT_F[7]=list_comb.d[[i]]$Wf_F[7]*list_comb.d[[i]]$Nb_F[7]  


# Calcul final percentage by species
list_comb.d[[i]]$Prc_F=list_comb.d[[i]]$WT_F/sum(list_comb.d[[i]]$WT_F)*100 

# Yield net kg/ha (by pond surface 0.05 ha)
## => [ Modify the 500m² values based on the pond surface area]
list_comb.d[[i]]$Rdt.net=((list_comb.d[[i]]$WT_F-list_comb.d[[i]]$WT_Stk)/1000)/0.05 



# Add economic value
# Calcul profitability by species
list_comb.d[[i]]$Profi=list_comb.d[[i]]$Rdt.net*list_comb.d[[i]]$Price.U 

# Duplicate the scenario name
## [c(6:7)=> modify based on the juvenile row]
list_comb.d[[i]]$scenario[c(6:7)]=list_comb.d[[i]]$scenario[1]


# Calcul Z
list_comb.d[[i]]$Z=-(log(list_comb.d[[i]]$Nb_F/list_comb.d[[i]]$Nb_Stk))

# Calcul mean number
list_comb.d[[i]]$Nb.mean=(list_comb.d[[i]]$Nb_Stk-list_comb.d[[i]]$Nb_F)/list_comb.d[[i]]$Z

# Calcul mean weight
list_comb.d[[i]]$W.mean=(list_comb.d[[i]]$Wi_Stk+list_comb.d[[i]]$Wf_F)/2 


# Calcul mean biomass
## Calcul mean biomass for adult group
list_comb.d[[i]]$B.g=list_comb.d[[i]]$Nb.mean*list_comb.d[[i]]$W.mean

## Calcul mean biomass for juvenil group
### Calcul mean biomass of Roach_juv 
list_comb.d[[i]]$B.g[6]=list_comb.d[[i]]$WT_F[6]/2 
### Calcul mean biomass of Tench_juv
list_comb.d[[i]]$B.g[7]=list_comb.d[[i]]$WT_F[7]/2 

# Calcul mean biomass in g/m2 (by pond surface 500m2)
## => [ Modify the 500m² values based on the pond surface area]
list_comb.d[[i]]$B.g.m2=list_comb.d[[i]]$B.g/500 

# Calcul mean biomass in dry weight
list_comb.d[[i]]$B_DW=list_comb.d[[i]]$B.g.m2*list_comb.d[[i]]$DW_rate


# Calcul biomass accumulation
list_comb.d[[i]]$BA.g=list_comb.d[[i]]$WT_F-list_comb.d[[i]]$WT_Stk 

# Calcul P:B
## Calcul P:B for adult group
list_comb.d[[i]]$`P/B`=list_comb.d[[i]]$BA.g/list_comb.d[[i]]$B.g+list_comb.d[[i]]$Z

## Calcul P:B for juv group
list_comb.d[[i]]$`P/B`[6]=list_comb.d[[i]]$BA.g[6]/list_comb.d[[i]]$B.g[6]
list_comb.d[[i]]$`P/B`[7]=list_comb.d[[i]]$BA.g[7]/list_comb.d[[i]]$B.g[7]

# Calcul Biomass acc in g/m2 (by pond surface 500m2)
list_comb.d[[i]]$Bacc.g.m2=list_comb.d[[i]]$BA.g/500 

# Calcul Biomass accumulate in dry weight
list_comb.d[[i]]$Baacc_DW=list_comb.d[[i]]$Bacc.g.m2*list_comb.d[[i]]$DW_rate

}



#add scenario + data feed
## [c(8:8)=> modify based on the feed row]
for (i in 1:length(scenarios)) {
 list_comb.d[[i]]=rbind(list_comb.d[[i]],data_ini.Feed)
 list_comb.d[[i]]$scenario[c(8:8)]=list_comb.d[[i]]$scenario[1] # [8] line for feed
}

for (i in 1:length(scenarios)) {
# For Feed group
## Calcul biomass
# #Calculate the biomass of feed : Total for each pond during all period 44 485g. Adjust this value to the surface area per m² by dividing by 500, then convert it to dry weight. Calculate the average by dividing by the duration.
list_comb.d[[i]]$B_DW[8]=44485/500*list_comb.d[[i]]$DW_rate[8]/list_comb.d[[i]]$Duration[8] 

## Calcul DetInput
# #Calculate the Detritus input of feed by multiplying the biomass of feed by the duration.
list_comb.d[[i]]$DetInput[8]=list_comb.d[[i]]$B_DW[8]*list_comb.d[[i]]$Duration[8] 

}


# Add economic value - feed value
## Calculate the profitability by substracting the fish profitability by the feed value ( which obtained by multiplying the total of feed biomass 44 485g.Dividing by 1000 to have the value in kg. Adjust this value to the surface area per ha by dividing by 0.0500, then multiply it by the price of the feed )

for (i in 1:length(scenarios)) {
list_comb.d[[i]]$Profi[1]=list_comb.d[[i]]$Profi[1] - ((44485)/1000)/0.05*list_comb.d[[i]]$Price.U[8] 
}


# Add resource group
## [c(9:13)=> modify based on the resource available row]
for (i in 1:length(scenarios)) {
 list_comb.d[[i]]=rbind(list_comb.d[[i]],data_ini.Rgroup)
 list_comb.d[[i]]$scenario[c(9:13)]=list_comb.d[[i]]$scenario[1]
}


# Loop to reorganize the rows of each dataframe in the list list_comb.d (feed and detritus at the end )
for (i in 1:length(list_comb.d)) {
  
  # Extract the current dataframe
  df <- list_comb.d[[i]]
  
  # Check if the dataframe has at least 13 rows
  if (nrow(df) >= 13) {
    # Extract the 5th row
    ligne_8 <- df[8, ]
    
    # Remove the 8th row from the original dataframe
    df <- df[-8, ]
    
    # Insert the 8th row at the 8th position
    df <- rbind(df[1:11, ], ligne_8, df[12:nrow(df), ])
  }
  
  # Update the dataframe in the list
  list_comb.d[[i]] <- df
}

list_comb.d.all=list_comb.d

# Put in dataframe

All_data=do.call(rbind.data.frame,list_comb.d.all)



# Ecopath for all scenario



# Install package
# remove.packages("Rpath")
# remotes::install_github('https://github.com/Purco/Rpath_fork.git')
# remotes::install_github('https://github.com/Purco/enaR.git')


# Run package
library(Rpath); library(data.table)

temps_debut <- system.time({

# start  
results_list <- list()
for (i in 1:length(scenarios)) {

# Groups and types for each functional group
## => [Modify and reorder  the functional group according to "list_comb.d"]
groups <- c('Grass_carp', 
            'Carp', 
            'Pike_perch', 
            'Roach',
            'Tench', 
            'Roach_juv', 
            'Tench_juv', 
            'MIB', 
            'Zooplancton',
            'Macrophyte',
            'Phytoplancton',
            'Feed',
            'Detritus')

## => [Modify and reorder  the functional group according to "list_comb.d"]
## => [0 for consumer, 1 for primary production, 2 for detritus and feed]
types  <- c(rep(0, 9), 1,1,2, 2)

## [13 => modify based on the total number of functional groups]
stgroups <- c(rep(0, 13))

REco.params <- create.rpath.params(group = groups, type = types,stgroup=stgroups)

REco.params$model[, Biomass := All_data[All_data$scenario==scenarios[i],]$B_DW]

REco.params$model[, PB := All_data[All_data$scenario==scenarios[i],]$`P/B`]

REco.params$model[, QB := All_data[All_data$scenario==scenarios[i],]$`C/B`]


#Biomass accumulation 
## [ => c(1:4) represents the fish groups;(0, 5) for other functional groups]
REco.params$model[, BioAcc  := c(All_data[All_data$scenario==scenarios[i],]$Baacc_DW[c(1:5)],rep(0, 8))]

# Unassimilated consumption
## [rep(0.2, 4) => for the fish groups;rep(0.4, 2) for MIB and Zoo; rep(0, 3) for other functional groups]
REco.params$model[, Unassim := c(rep(0.2, 7), rep(0.4, 2), rep(0, 4))]

# Detritus import
#add value from feed
REco.params$model[, DetInput := All_data[All_data$scenario==scenarios[i],]$DetInput]

#Detrital Fate
REco.params$model[, Detritus := c(rep(1, 11), rep(1, 2))]

## Add second detrital Fate for feed
REco.params$model[, Feed := c(rep(0, 11),1,0)] # Add second det (PR)


# Diet

REco.params$diet[, Grass_carp        := c(NA,NA,NA,NA,NA,0.000,0.000,0.040,0.120,0.190,0.210,0.250,0.200,NA)]
 
REco.params$diet[, Carp              := c(NA,NA,NA,NA,NA, 0.000,0.000,0.020,0.050,0.020,0.030,0.850,0.030,NA)]
                 
REco.params$diet[, Pike_perch        := c(NA,NA,NA,NA,NA, 0.060,0.060,0.480,0.200,0.000,0.000,0.200,0.000,NA)]
 
REco.params$diet[, Roach             := c(NA,NA,NA,NA,NA, 0.060,0.070,0.110,0.120,0.100,0.170,0.250,0.120,NA)]

REco.params$diet[, Tench             := c(NA,NA,NA,NA,NA, 0.060,0.060,0.110,0.140,0.120,0.140,0.250,0.130,NA)]

REco.params$diet[, Roach_juv         := c(NA,NA,NA,NA,NA,0.000,0.000,0.200,0.250,0.200,0.200,0.000,0.150,NA)]

REco.params$diet[, Tench_juv         := c(NA,NA,NA,NA,NA,0.000,0.000,0.200,0.250,0.200,0.200,0.000,0.150,NA)]

REco.params$diet[, MIB               := c(NA,NA,NA,NA,NA,0.000,0.000,0.000,0.090,0.190,0.320,0.150,0.250,NA)]

REco.params$diet[, Zooplancton       := c(NA,NA,NA,NA,NA,0.000,0.000,0.000,0.590,0.410,0.000,0.000,0.000,NA)]


REco <- rpath(REco.params, eco.name = 'R Ecosystem')
## [13 => modify based on the total number of functional groups]
results_list[[i]]=cbind(data.frame(REco[c(4:13,15)]),data.frame(Scena = rep(scenarios[i], 13)))
}

All_results=do.call(rbind.data.frame,results_list)

All_results_sc=cbind(All_results,All_data)

# end
})
temps_ecoule <- temps_debut["elapsed"]
print(temps_ecoule)




# EnaR



temps_debut <- system.time({

# start  
res.enaR_list <- list()
for (k in 1:length(scenarios)) {
  
# Steps of Rpath to enaR (network) conversion:
# Set up: pull in group names, count number of living vs. non-living groups
groups <- as.vector(REco$Group)
nliving <- nrow(REco.params$model[Type <  2, ])
ndead   <- nrow(REco.params$model[Type == 2, ])


# Calculate consumption values from diet matrix: DC*QB*Biomass

diet<-REco$DC
QQ<-matrix(nrow = (nliving + ndead + 1),ncol=nliving)
for (j in 1:nliving){
QQ[,j]<-diet[,j]*results_list[[k]]$QB[j]*results_list[[k]]$Biomass[j]
}

# Ignore imports in diet matrix
QQ<-QQ[1:(nliving+ndead),]#change (PR)

# Name the consumption matrix
colnames(QQ)<-groups[1:nliving]
rownames(QQ)<-groups[1:(nliving+ndead)]#change (PR)
# <Deal with discards>

# Calculate flow to detritus (first need to calculate M0 values for each node), append to diet matrix
M0<-results_list[[k]]$PB*(1-results_list[[k]]$EE)

Detritus<-(M0*results_list[[k]]$Biomass+results_list[[k]]$QB*results_list[[k]]$Biomass*results_list[[k]]$Unassim)*REco$DetFate[,ndead]#change (PR)
Feed<-(M0*REco$Biomass+REco$QB*REco$Biomass*REco$Unassim)*REco$DetFate[,1]#Add (PR)

Detritus[(nliving+ndead)]<-0 #change (PR)
Feed[(nliving+1)]<-0 #Add (PR)

QQ<-cbind(QQ,Feed,Detritus)#change (PR)

# Calculate exports: catch, positive biomass accumulation, detrital production
Export<-(ifelse(results_list[[k]]$BA>0,results_list[[k]]$BA,0))
Export<-Export[1:(nliving+ndead)]



for (i in 1:ndead){
  Export[nliving+i]<-M0[(nliving+i)]*results_list[[k]]$Biomass[(nliving+i)]-sum(Export[1:nliving])
}


# Calculate respiration, assuming detrital groups have 0 respiration
Resp<-((1-results_list[[k]]$Unassim)*results_list[[k]]$QB-results_list[[k]]$PB)*results_list[[k]]$Biomass
Resp<-ifelse(Resp>0,Resp,0)
Resp<-Resp[1:(nliving+ndead)]

Resp[(nliving+ndead):(nliving+ndead)]<-0 #change (PR)


# Estimate respiration of primary producers


gross<-0

## [c(10:11) =>  c(10:11) represents the primary production row; adjust this column according to the corresponding row in the data]
Resp[c(10:11)]<-0 #change (PR)

# Calculate imports: negative biomass accumulation, grosspp

Import<-abs(ifelse(results_list[[k]]$BA<0,results_list[[k]]$BA,0))
## [c(10:11) =>  c(10:11) represents the primary production row; adjust this column according to the corresponding row in the data]
Import[c(10:11)]<-gross #change (PR)
Import<-Import[1:(nliving+ndead)]

# Assign biomass values 
Biomass<-results_list[[k]]$Biomass[1:(nliving+ndead)]

# Pack the model

# install.packages("gdata", repos = "https://packagemanager.posit.co/cran/2023-05-06")
# update.packages(ask = FALSE)

# remotes::install_github('Purco/enaR')

library(enaR)



orig.network<-enaR::pack(flow = QQ,
                        input = Import,
                        export = Export,
                        living = c(rep(TRUE,nliving),rep(FALSE,ndead)),
                        respiration = Resp,
                        storage = Biomass)

res.enaR_list[[k]]=merge(results_list[[k]],data.frame(t(enaFlow(orig.network)$ns[,c(2,3,5)])))
}

All_enar.res=do.call(rbind.data.frame,res.enaR_list)

All_enar.res_sc=cbind(All_enar.res,All_data)

# end
})
temps_ecoule <- temps_debut["elapsed"]
print(temps_ecoule)

#print result
write.csv(All_enar.res_sc,"All_enar_res_simul.csv")
```



# Visualisation of resultats

```{r,echo=FALSE,warning = FALSE,message = FALSE}
library(stringr)
All_enar.res_sc$scena1 <- str_extract(All_enar.res_sc$Scena, "\\d+$")
```

## Number of scenario
```{r,echo=FALSE,warning = FALSE,message = FALSE}

length(unique(All_enar.res_sc$scena1))
```


## Summary

```{r,echo=FALSE,warning = FALSE,message = FALSE}
Rdt.All_enar.res_sc=All_enar.res_sc%>%group_by(scenario,scena1)%>% summarise(RDT=sum(Rdt.net,na.rm = T),FCI=mean(FCI),Profitability=sum(Profi,na.rm = T),n=n())


# Reorganize and display according to the scenario number
All_enar.res_sc_ord <- All_enar.res_sc %>%
  group_by(scenario, scena1) %>%
  summarise(
    RDT = sum(Rdt.net, na.rm = TRUE),
    FCI = mean(FCI),
    Profitability = sum(Profi, na.rm = TRUE),
    n = n(),
    .groups = "drop"
  ) %>%
  mutate(scena1_num = as.numeric(gsub("\\D", "", scena1))) %>%  # extrait les chiffres
  arrange(scena1_num)


summary_stats <- All_enar.res_sc_ord %>%
  summarise(
    RDT_min = min(RDT, na.rm = TRUE),
    RDT_max = max(RDT, na.rm = TRUE),
    RDT_mean = mean(RDT, na.rm = TRUE),
    RDT_sd = sd(RDT, na.rm = TRUE),

    FCI_min = min(FCI, na.rm = TRUE),
    FCI_max = max(FCI, na.rm = TRUE),
    FCI_mean = mean(FCI, na.rm = TRUE),
    FCI_sd = sd(FCI, na.rm = TRUE),

    Profit_min = min(Profitability, na.rm = TRUE),
    Profit_max = max(Profitability, na.rm = TRUE),
    Profit_mean = mean(Profitability, na.rm = TRUE),
    Profit_sd = sd(Profitability, na.rm = TRUE)
  )
summary_stats
```



### Summary

```{r,echo=FALSE,warning = FALSE,message = FALSE,fig.width=7,fig.height=2}
library(dplyr)

# Filtrer les groupes et calculer les statistiques
data_EEAll1 <- All_enar.res_sc %>%
  filter(Group %in% c("Roach_juv","Tench_juv","MIB", "Zooplankton", "Phytoplankton", "Detritus", "Feed")) %>%
  group_by(Group) %>%
  summarise(
    Minimum = min(EE, na.rm = TRUE),
    Maximum = max(EE, na.rm = TRUE),
    Moyenne = mean(EE, na.rm = TRUE),
    CV = sd(EE, na.rm = TRUE) / mean(EE, na.rm = TRUE)
  )
data_EEAll1
```



## Net yield
```{r,echo=FALSE,warning = FALSE,message = FALSE}
library(tidyverse)
Rdt.All_enar.res_sc=All_enar.res_sc%>%group_by(scenario,scena1)%>% summarise(RDT=sum(Rdt.net,na.rm = T),FCI=mean(FCI),Profitability=sum(Profi,na.rm = T),n=n())


## # Reorganize and display according to the scenario number

All_enar.res_sc_ord <- All_enar.res_sc %>%
  group_by(scenario, scena1) %>%
  summarise(
    RDT = sum(Rdt.net, na.rm = TRUE),
    FCI = mean(FCI),
    Profitability = sum(Profi, na.rm = TRUE),
    n = n(),
    .groups = "drop"
  ) %>%
  mutate(scena1_num = as.numeric(gsub("\\D", "", scena1))) %>%  # extrait les chiffres
  arrange(scena1_num)


## Ordre 1-> 3876 

All_enar.res_sc_ord <- All_enar.res_sc_ord %>%
  mutate(scena1_num = factor(scena1_num, levels = as.character(1:3876)))

ggplot(All_enar.res_sc_ord,aes(x =scena1_num,y=RDT))+
  geom_point()+
  theme_bw() +
  theme(
    axis.line = element_line(colour = "black"),
    legend.key = element_blank(),
    panel.background = element_rect(fill = NA),
    panel.grid = element_blank(),
    panel.spacing = unit(0.1, "lines"),
    strip.text = element_text(color="black",size = 12),
    axis.text = element_text(color="black",size = 13),
    axis.title = element_text(color="black",size = 16,face="bold"),
    legend.title = element_text(color="black",size = 14,face="bold"),
    legend.text = element_text(color="black",size = 13,face="bold")
      )+
  labs(x="Scenario",y="Net yield (kg/ha)")
```




## Profitability 

```{r,echo=FALSE,warning = FALSE,message = FALSE}

ggplot(All_enar.res_sc_ord,aes(x =scena1_num,y=Profitability))+
  geom_point()+
  theme_bw() +
  theme(
    axis.line = element_line(colour = "black"),
    legend.key = element_blank(),
    panel.background = element_rect(fill = NA),
    # panel.grid.major = element_line(colour = "grey75",size=0.5),
    # panel.grid.minor = element_line(colour = "grey75",size=0.2),
     panel.grid = element_blank(),
    panel.spacing = unit(0.1, "lines"),
    strip.text = element_text(color="black",size = 12),
    axis.text = element_text(color="black",size = 13),
    # axis.text.x = element_text(color="black",size = 13,angle=30,hjust=1),
    axis.title = element_text(color="black",size = 16,face="bold"),
    legend.title = element_text(color="black",size = 14,face="bold"),
    legend.text = element_text(color="black",size = 13,face="bold")
      )+
  labs(x="Scenario",y="Profitability ($/ha)")
```


## MIB

```{r,echo=FALSE,warning = FALSE,message = FALSE}
All_enar.res_sc <- All_enar.res_sc %>%
  mutate(scena2 = factor(ceiling(row_number() / 9), levels = 1:3876))
ggplot(All_enar.res_sc[All_enar.res_sc$Group=="MIB",],aes(x =scena2,y=EE))+
  geom_point()+
  theme_bw() +
  theme(
    axis.line = element_line(colour = "black"),
    legend.key = element_blank(),
    panel.background = element_rect(fill = NA),
     panel.grid = element_blank(),
    panel.spacing = unit(0.1, "lines"),
    strip.text = element_text(color="black",size = 12),
    axis.text = element_text(color="black",size = 13),
    axis.title = element_text(color="black",size = 16,face="bold"),
    legend.title = element_text(color="black",size = 14,face="bold"),
    legend.text = element_text(color="black",size = 13,face="bold")
      )+
  labs(x="Scenario",y="EE_Macroinvertebrate")
```



## Zooplankton

```{r,echo=FALSE,warning = FALSE,message = FALSE}
ggplot(All_enar.res_sc[All_enar.res_sc$Group=="Zooplancton",],aes(x =scena2,y=EE))+
  geom_point()+
  theme_bw() +
  theme(
    axis.line = element_line(colour = "black"),
    legend.key = element_blank(),
    panel.background = element_rect(fill = NA),
    panel.grid = element_blank(),
    panel.spacing = unit(0.1, "lines"),
    strip.text = element_text(color="black",size = 12),
    axis.text = element_text(color="black",size = 13),
    # axis.text.x = element_text(color="black",size = 13,angle=30,hjust=1),
    axis.title = element_text(color="black",size = 16,face="bold"),
    legend.title = element_text(color="black",size = 14,face="bold"),
    legend.text = element_text(color="black",size = 13,face="bold")
      )+
  labs(x="Scenario",y="EE_Zooplancton")

```


## Phytoplankton

```{r,echo=FALSE,warning = FALSE,message = FALSE}
ggplot(All_enar.res_sc[All_enar.res_sc$Group=="Phytoplancton",],aes(x =scena2,y=EE))+
  geom_point()+
  theme_bw() +
  theme(
    axis.line = element_line(colour = "black"),
    legend.key = element_blank(),
    panel.background = element_rect(fill = NA),
    # panel.grid.major = element_line(colour = "grey75",size=0.5),
    # panel.grid.minor = element_line(colour = "grey75",size=0.2),
     panel.grid = element_blank(),
    panel.spacing = unit(0.1, "lines"),
    strip.text = element_text(color="black",size = 12),
    axis.text = element_text(color="black",size = 13),
    # axis.text.x = element_text(color="black",size = 13,angle=30,hjust=1),
    axis.title = element_text(color="black",size = 16,face="bold"),
    legend.title = element_text(color="black",size = 14,face="bold"),
    legend.text = element_text(color="black",size = 13,face="bold")
      )+
  labs(x="Scenario",y="EE_Phytoplancton")

```


## Detritus

```{r,echo=FALSE,warning = FALSE,message = FALSE}
ggplot(All_enar.res_sc[All_enar.res_sc$Group=="Detritus",],aes(x =scena2,y=EE))+
  geom_point()+
  theme_bw() +
  theme(
    axis.line = element_line(colour = "black"),
    legend.key = element_blank(),
    panel.background = element_rect(fill = NA),
    # panel.grid.major = element_line(colour = "grey75",size=0.5),
    # panel.grid.minor = element_line(colour = "grey75",size=0.2),
     panel.grid = element_blank(),
    panel.spacing = unit(0.1, "lines"),
    strip.text = element_text(color="black",size = 12),
    axis.text = element_text(color="black",size = 13),
    # axis.text.x = element_text(color="black",size = 13,angle=30,hjust=1),
    axis.title = element_text(color="black",size = 16,face="bold"),
    legend.title = element_text(color="black",size = 14,face="bold"),
    legend.text = element_text(color="black",size = 13,face="bold")
      )+
  labs(x="Scenario",y="EE_Detritus")

```


## Feed


```{r,echo=FALSE,warning = FALSE,message = FALSE}
ggplot(All_enar.res_sc[All_enar.res_sc$Group=="Feed",],aes(x =scena2,y=EE))+
  geom_point()+
  theme_bw() +
  theme(
    axis.line = element_line(colour = "black"),
    legend.key = element_blank(),
    panel.background = element_rect(fill = NA),
   panel.grid = element_blank(),
    panel.spacing = unit(0.1, "lines"),
    strip.text = element_text(color="black",size = 12),
    axis.text = element_text(color="black",size = 13),
    axis.title = element_text(color="black",size = 16,face="bold"),
    legend.title = element_text(color="black",size = 14,face="bold"),
    legend.text = element_text(color="black",size = 13,face="bold")
      )+
  labs(x="Scenario",y="EE_Feed")

```




## FCI

```{r,echo=FALSE,warning = FALSE,message = FALSE}
ggplot(All_enar.res_sc[All_enar.res_sc$Group=="Grass_carp",],aes(x =scena2,y=FCI))+
  geom_point()+
  theme_bw() +
  theme(
    axis.line = element_line(colour = "black"),
    legend.key = element_blank(),
    panel.background = element_rect(fill = NA),
     panel.grid = element_blank(),
    panel.spacing = unit(0.1, "lines"),
    strip.text = element_text(color="black",size = 12),
    axis.text = element_text(color="black",size = 13),
     axis.title = element_text(color="black",size = 16,face="bold"),
    legend.title = element_text(color="black",size = 14,face="bold"),
    legend.text = element_text(color="black",size = 13,face="bold")
      )+
  labs(x="Scenario",y="FCI")

```


# Boxplot

## EE
```{r,echo=FALSE,warning = FALSE,message = FALSE,fig.width=16, fig.height=10}
ggplot(All_enar.res_sc[All_enar.res_sc$Group%in%c("Roach_juv","Tench_juv","MIB","Zooplancton","Phytoplancton","Feed","Detritus"),], aes(x=EE, y=Group)) +
  geom_boxplot() +
  scale_x_continuous(breaks = function(x) seq(floor(min(x)), ceiling(max(x)), by = 0.5))+
  stat_boxplot(geom="errorbar",width=0.5, coef=NULL)+
  stat_summary(fun.y=mean, geom="point", shape=20, size=2, color="red", fill="red") +
  theme_bw() +
  theme(
   axis.line = element_line(colour = "black"),
    legend.key = element_blank(),
    panel.background = element_rect(fill = NA),
    # panel.grid.major = element_line(colour = "grey75",size=0.5),
    # panel.grid.minor = element_line(colour = "grey75",size=0.2),
    panel.grid = element_blank(),
    panel.spacing = unit(0.1, "lines"),
    strip.text = element_text(color="black",size = 12),
    axis.text = element_text(color="black",size = 13),
    # axis.text.x = element_text(color="black",size = 13,angle=30,hjust=1),
    axis.title = element_text(color="black",size = 16,face="bold"),
    legend.title = element_text(color="black",size = 14,face="bold"),
    legend.text = element_text(color="black",size = 13,face="bold")
      )+
  labs(y="Group",x="Ecotrophic efficiency")
```



# Screening scenario 

## Select the fish species with performance indicators (Ecotrophic efficiency, net yield, Finn Cycling Index)


```{r,echo=FALSE,warning = FALSE,message = FALSE}
# Scenario
slct.scn= All_enar.res_sc[!All_enar.res_sc$Group%in%c("Roach_juv","Tench_juv","MIB","Zooplancton","Macrophyte","Phytoplancton","Feed","Detritus"),c(1,46,49,48)] %>% pivot_wider(names_from="Group", values_from="prc_scn")

## rename
slct.scn<- slct.scn %>%
  rename(prc.Grass_carp = Grass_carp,
         prc.Common_carp = Carp,
         prc.Pike_perch = Pike_perch,
         prc.Roach = Roach,
         prc.Tench=Tench)


# EE
slct.EE= All_enar.res_sc[!All_enar.res_sc$Group%in%c("Grass_carp","Carp","Pike_perch","Roach","Tench"),c(1,7,46,49)] %>% pivot_wider(names_from="Group", values_from="EE")

## rename
slct.EE<- slct.EE %>%
  rename(EE.Roach_juv = Roach_juv,
         EE.Tench_juv = Tench_juv,
         EE.Macroinvertebrate = MIB,
         EE.Zooplancton=Zooplancton,
         EE.Macrophyte=Macrophyte,
         EE.Phytoplancton=Phytoplancton,
         EE.Detritus=Detritus)

# Rdt et FCI

# Merge
merge.All_enar.res_sc=merge(slct.scn,slct.EE)
merge.All_enar.res_sc=merge(merge.All_enar.res_sc,Rdt.All_enar.res_sc)

```

```{r,echo=FALSE,warning = FALSE,message = FALSE}
write.csv(merge.All_enar.res_sc,"merge.All_enar.res_Simul.csv")
```




